---
title: '"Thesis" Manuscript'
author: "Carter E. Watson"
date: "2025-07-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load All Required Packages

```{r packages}
require(tidyverse)
require(dplyr)
require(sf)
require(ggpubr)
require(scico)
require(ncdf4)
require(geosphere)
require(RColorBrewer)
require(ggnewscale)
require(knitr)
require(emmeans)
```


## Map Code (Infrastructure to run other cells)

```{r pressure, include=FALSE}
states <- st_read("./data/geography/cb_2018_us_state_500k.shp")
physiographic <- st_make_valid(st_read("./data/geography/physio_shp/physio.shp"))
selected_states <- states %>% 
  filter(NAME %in% c("Ohio", "Kentucky", "North Carolina", "Virginia", "West Virginia", "Tennessee"))
clipped_physiographic <- st_intersection(physiographic, selected_states)
box_coords <- data.frame(
  long = c(-82.878, -79.425, -79.652, -82.991, -82.878),
  lat = c(38.967, 38.830, 36.141, 36.274, 38.967))
box_polygon <- st_polygon(list(cbind(box_coords$long, box_coords$lat))) %>% 
  st_sfc(crs = st_crs(clipped_physiographic))
inside_regions <- st_intersection(clipped_physiographic, box_polygon) #WHERE THE STATES AND THE BOX OVERLAP.
outside_regions <- st_difference(clipped_physiographic, box_polygon) #OUTSIDE WHERE THE STATES AND BOX OVERLAP
inside_colors <- colorRampPalette(brewer.pal(9, "Greens"))(length(unique(inside_regions$PROVINCE))) #MAKE IT GREEN INSIDE.
outside_colors <- colorRampPalette(brewer.pal(9, "Blues"))(length(unique(outside_regions$PROVINCE))) #AND BLUE OUTSIDE.
inside_palette <- setNames(inside_colors, unique(inside_regions$PROVINCE)) #MAKE THE KEY FOR INSIDE THE BOX.
outside_palette <- setNames(outside_colors, unique(outside_regions$PROVINCE)) #AND THE KEY FOR OUTSIDE THE BOX.
outside_regions <- outside_regions %>% mutate(color = outside_palette[PROVINCE]) %>%
  group_by(color) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup()
inside_regions <- inside_regions %>% mutate(color = inside_palette[PROVINCE]) %>%
  group_by(color) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup()
combined_regions <- bind_rows(
  inside_regions,
  outside_regions)
selected_states <- st_transform(selected_states, crs = 4326)
combined_regions <- st_transform(combined_regions, crs = 4326)

standardized_theme <- theme(legend.text = element_text(size = 10), legend.title = element_text(size = 12), legend.key.width = unit(1.5, 'cm'),
                            plot.title = element_text(hjust = 0.5, face="bold"))
```


## MAKING INSIDE DEFORESTATION DATA FRAME:

```{r}
inside_18.001 <- read.csv("./data/csvs/deforested/December2025_18.001_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(-X)
inside_18.002 <- read.csv("./data/csvs/deforested/December2025_18.002_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(-X)
inside_18.003 <- read.csv("./data/csvs/deforested/December2025_18.003_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(-X)
inside_18.004 <- read.csv("./data/csvs/deforested/December2025_18.004_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(-X)
inside_18.005 <- read.csv("./data/csvs/deforested/December2025_18.005_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(-X)
inside_18.006 <- read.csv("./data/csvs/deforested/December2025_18.006_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(-X)

inside_17.001 <- read.csv("./data/csvs/deforested/December2025_17.001_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(-X)
inside_17.002 <- read.csv("./data/csvs/deforested/December2025_17.002_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(-X)
inside_17.003 <- read.csv("./data/csvs/deforested/December2025_17.003_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(-X)
inside_17.004 <- read.csv("./data/csvs/deforested/December2025_17.004_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(-X)
inside_17.005 <- read.csv("./data/csvs/deforested/December2025_17.005_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(-X)
inside_17.006 <- read.csv("./data/csvs/deforested/December2025_17.006_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(-X)
inside <- bind_rows(inside_18.001, inside_18.002, inside_18.003, inside_18.004, inside_18.005, inside_18.006, inside_17.001, inside_17.002, inside_17.003, inside_17.004, inside_17.005, inside_17.006)

inside_ALBEDO_SWDOWN_18.001 <- read.csv("./data/csvs/deforested/December2025_18.001_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(-X)
inside_ALBEDO_SWDOWN_18.002 <- read.csv("./data/csvs/deforested/December2025_18.002_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(-X)
inside_ALBEDO_SWDOWN_18.003 <- read.csv("./data/csvs/deforested/December2025_18.003_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(-X)
inside_ALBEDO_SWDOWN_18.004 <- read.csv("./data/csvs/deforested/December2025_18.004_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(-X)
inside_ALBEDO_SWDOWN_18.005 <- read.csv("./data/csvs/deforested/December2025_18.005_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(-X)
inside_ALBEDO_SWDOWN_18.006 <- read.csv("./data/csvs/deforested/December2025_18.006_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(-X)

inside_ALBEDO_SWDOWN_17.001 <- read.csv("./data/csvs/deforested/December2025_17.001_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(-X)
inside_ALBEDO_SWDOWN_17.002 <- read.csv("./data/csvs/deforested/December2025_17.002_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(-X)
inside_ALBEDO_SWDOWN_17.003 <- read.csv("./data/csvs/deforested/December2025_17.003_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(-X)
inside_ALBEDO_SWDOWN_17.004 <- read.csv("./data/csvs/deforested/December2025_17.004_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(-X)
inside_ALBEDO_SWDOWN_17.005 <- read.csv("./data/csvs/deforested/December2025_17.005_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(-X)
inside_ALBEDO_SWDOWN_17.006 <- read.csv("./data/csvs/deforested/December2025_17.006_ALBEDO_SWDOWN_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(-X)
inside_ALBEDO_SWDOWN <- bind_rows(inside_ALBEDO_SWDOWN_18.001, inside_ALBEDO_SWDOWN_18.002, inside_ALBEDO_SWDOWN_18.003, inside_ALBEDO_SWDOWN_18.004, inside_ALBEDO_SWDOWN_18.005, inside_ALBEDO_SWDOWN_18.006, inside_ALBEDO_SWDOWN_17.001, inside_ALBEDO_SWDOWN_17.002, inside_ALBEDO_SWDOWN_17.003, inside_ALBEDO_SWDOWN_17.004, inside_ALBEDO_SWDOWN_17.005, inside_ALBEDO_SWDOWN_17.006)


inside_VERTICAL_WS_18.001 <- read.csv("./data/csvs/July2025/July2025_18.001_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_18.002 <- read.csv("./data/csvs/July2025/July2025_18.002_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_18.003 <- read.csv("./data/csvs/July2025/July2025_18.003_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_18.004 <- read.csv("./data/csvs/July2025/July2025_18.004_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_18.005 <- read.csv("./data/csvs/July2025/July2025_18.005_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_18.006 <- read.csv("./data/csvs/July2025/July2025_18.006_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)

inside_VERTICAL_WS_17.001 <- read.csv("./data/csvs/July2025/July2025_17.001_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_17.002 <- read.csv("./data/csvs/July2025/July2025_17.002_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_17.003 <- read.csv("./data/csvs/July2025/July2025_17.003_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_17.004 <- read.csv("./data/csvs/July2025/July2025_17.004_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_17.005 <- read.csv("./data/csvs/July2025/July2025_17.005_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS_17.006 <- read.csv("./data/csvs/July2025/July2025_17.006_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
inside_VERTICAL_WS <- bind_rows(inside_VERTICAL_WS_18.001, inside_VERTICAL_WS_18.002, inside_VERTICAL_WS_18.003, inside_VERTICAL_WS_18.004, inside_VERTICAL_WS_18.005, inside_VERTICAL_WS_18.006, inside_VERTICAL_WS_17.001, inside_VERTICAL_WS_17.002, inside_VERTICAL_WS_17.003, inside_VERTICAL_WS_17.004, inside_VERTICAL_WS_17.005, inside_VERTICAL_WS_17.006)


inside <- full_join(inside, inside_ALBEDO_SWDOWN, by = c("Latitude", "Longitude", "treatment", "year", "tLU_INDEX", "cLU_INDEX"))
inside <- full_join(inside, inside_VERTICAL_WS, by = c("Latitude", "Longitude", "treatment", "year", "tLU_INDEX", "cLU_INDEX"))

rm(inside_ALBEDO_SWDOWN, inside_VERTICAL_WS, inside_VERTICAL_WS_17.001, inside_VERTICAL_WS_17.002, inside_VERTICAL_WS_17.003, inside_VERTICAL_WS_17.004, inside_VERTICAL_WS_17.005, inside_VERTICAL_WS_17.006,  inside_VERTICAL_WS_18.001, inside_VERTICAL_WS_18.002, inside_VERTICAL_WS_18.003, inside_VERTICAL_WS_18.004, inside_VERTICAL_WS_18.005, inside_VERTICAL_WS_18.006, inside_ALBEDO_SWDOWN_17.001, inside_ALBEDO_SWDOWN_17.002, inside_ALBEDO_SWDOWN_17.003, inside_ALBEDO_SWDOWN_17.004, inside_ALBEDO_SWDOWN_17.005, inside_ALBEDO_SWDOWN_17.006, inside_ALBEDO_SWDOWN_18.001, inside_ALBEDO_SWDOWN_18.002, inside_ALBEDO_SWDOWN_18.003, inside_ALBEDO_SWDOWN_18.004, inside_ALBEDO_SWDOWN_18.005, inside_ALBEDO_SWDOWN_18.006, inside_17.001, inside_17.002, inside_17.003, inside_17.004, inside_17.005, inside_17.006, inside_18.001, inside_18.002, inside_18.003, inside_18.004, inside_18.005, inside_18.006)

## MAKING THETA BUCKETS INSIDE##
calculate_polar <- function(lat, lon) {
  r <- distHaversine(c(-81.21869, 37.57799), c(lon, lat))
  theta <- atan2(lat - 37.57799, lon - -81.21869)
  return(c(r, theta))}
inside <- inside %>% rowwise() %>%
  mutate(polar = list(calculate_polar(Latitude, Longitude)),
         r_km = (polar[1]/1000),
         theta = polar[2]) %>%
  select(-polar) %>% ungroup()
inside <- inside %>% mutate(theta_bucket = case_when(theta >= 0 & theta < pi/4 ~ "bucket1",
                                                           theta >= pi/4 & theta < pi/2 ~ "bucket2",
                                                           theta >= pi/2 & theta < 3*pi/4 ~ "bucket3",
                                                           theta >= 3*pi/4 & theta <= pi ~ "bucket4",
                                                           theta < -3*pi/4 & theta >= -pi ~ "bucket5",
                                                           theta < -pi/2 & theta >= -3*pi/4 ~ "bucket6",
                                                           theta < -pi/4 & theta >= -pi/2 ~ "bucket7",
                                                           theta < 0 & theta >= -pi/4 ~ "bucket8"))

## ADDING IN SOIL TYPE & ELEVATION##
nc_whatever <- nc_open("./data/netCDF_files/wrfout_2017_control_domain.nc")
lat <- ncvar_get(nc_whatever, "XLAT")
lon <- ncvar_get(nc_whatever, "XLONG")
elevation <- matrix(0, nrow = dim(lat)[1], ncol = dim(lat)[2])
for (i in 1:100) {
  for (j in 1:100) {
    elevation[i, j] <- ncvar_get(nc_whatever, "HGT", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
soil_type <- matrix(0, nrow = dim(lat)[1], ncol = dim(lat)[2])
for (i in 1:100) {
  for (j in 1:100) {
    soil_type[i, j] <- ncvar_get(nc_whatever, "ISLTYP", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
full_table <- data.frame(
  Longitude = as.vector(lon),
  Latitude = as.vector(lat),
  ELEVATION = as.vector(elevation),
  SOIL.TYPE = as.vector(soil_type))
nc_close(nc_whatever)
rm(lat, lon, elevation, soil_type)
full_table <- full_table %>%
  mutate(SOIL.TYPE = ifelse(SOIL.TYPE %in% c(2,8,11,14,16), 1, SOIL.TYPE)) %>% 
  mutate(SOIL.TYPE = recode(SOIL.TYPE, '1' = "Other", '3' = "Sandy Loam", '4' = "Silt Loam", '6' = "Loam"))
prop.table(table(full_table$SOIL.TYPE))

full_table2 <- full_table %>% mutate(Latitude = round(Latitude, 4), Longitude = round(Longitude, 4))

inside <- inside %>% mutate(Latitude = round(Latitude, 4), Longitude = round(Longitude, 4))

inside <- full_join(inside, full_table2, by = c("Latitude", "Longitude"))
inside <- inside %>% filter(!is.na(Mean_CTRL_ET)) %>% filter(Mean_CTRL_PSN > 2)

## CREATING NORM() REGRESSIONS
inside <- inside %>% mutate(normalized_ctrl_SW = Mean_CTRL_SWDOWN / mean(Mean_CTRL_SWDOWN, na.rm = TRUE) - 1,
                            normalized_ctrl_GT = Mean_CTRL_GT / mean(Mean_CTRL_GT, na.rm = TRUE) - 1,
                            normalized_ctrl_VPD = Mean_CTRL_VPD / mean(Mean_CTRL_VPD, na.rm = TRUE) - 1,
                            normalized_ctrl_SM = Mean_CTRL_SMOIS / mean(Mean_CTRL_SMOIS, na.rm = TRUE) - 1,
                            normalized_ctrl_ET = Mean_CTRL_ET / mean(Mean_CTRL_ET, na.rm = TRUE) - 1,
                            normalized_ctrl_PRCP = Mean_CTRL_RAINNC / mean(Mean_CTRL_RAINNC, na.rm = TRUE) - 1,
                            normalized_ctrl_W = Mean_CTRL_W / mean(Mean_CTRL_W, na.rm = TRUE) - 1)
```


## CONSTRUCTING OUTSIDE DATA FRAME

```{r}
outside_luc1.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.001_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 1)
outside_luc2.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.002_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 2)
outside_luc3.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.003_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 3)
outside_luc4.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.004_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 4)
outside_luc5.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.005_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 5)
outside_luc6.17 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.006_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 6)
outside_luc1.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.001_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 1)
outside_luc2.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.002_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 2)
outside_luc3.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.003_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 3)
outside_luc4.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.004_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 4)
outside_luc5.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.005_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 5)
outside_luc6.18 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.006_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 6)
outside <- bind_rows(outside_luc1.17, outside_luc2.17, outside_luc3.17, outside_luc4.17, outside_luc5.17, outside_luc6.17,
                    outside_luc1.18, outside_luc2.18, outside_luc3.18, outside_luc4.18, outside_luc5.18, outside_luc6.18)

outside_ALBEDO_SWDOWN_18.001 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.001_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(-X)
outside_ALBEDO_SWDOWN_18.002 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.002_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(-X)
outside_ALBEDO_SWDOWN_18.003 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.003_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(-X)
outside_ALBEDO_SWDOWN_18.004 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.004_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(-X)
outside_ALBEDO_SWDOWN_18.005 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.005_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(-X)
outside_ALBEDO_SWDOWN_18.006 <- read.csv("./data/csvs/remaining_deciduous/December2025_18.006_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(-X)

outside_ALBEDO_SWDOWN_17.001 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.001_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(-X)
outside_ALBEDO_SWDOWN_17.002 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.002_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(-X)
outside_ALBEDO_SWDOWN_17.003 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.003_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(-X)
outside_ALBEDO_SWDOWN_17.004 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.004_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(-X)
outside_ALBEDO_SWDOWN_17.005 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.005_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(-X)
outside_ALBEDO_SWDOWN_17.006 <- read.csv("./data/csvs/remaining_deciduous/December2025_17.006_ALBEDO_SWDOWN_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(-X)
outside_ALBEDO_SWDOWN <- bind_rows(outside_ALBEDO_SWDOWN_18.001, outside_ALBEDO_SWDOWN_18.002, outside_ALBEDO_SWDOWN_18.003, outside_ALBEDO_SWDOWN_18.004, outside_ALBEDO_SWDOWN_18.005, outside_ALBEDO_SWDOWN_18.006, outside_ALBEDO_SWDOWN_17.001, outside_ALBEDO_SWDOWN_17.002, outside_ALBEDO_SWDOWN_17.003, outside_ALBEDO_SWDOWN_17.004, outside_ALBEDO_SWDOWN_17.005, outside_ALBEDO_SWDOWN_17.006)


outside_VERTICAL_WS_18.001 <- read.csv("./data/csvs/July2025/July2025_18.001_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_18.002 <- read.csv("./data/csvs/July2025/July2025_18.002_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_18.003 <- read.csv("./data/csvs/July2025/July2025_18.003_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_18.004 <- read.csv("./data/csvs/July2025/July2025_18.004_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_18.005 <- read.csv("./data/csvs/July2025/July2025_18.005_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_18.006 <- read.csv("./data/csvs/July2025/July2025_18.006_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)

outside_VERTICAL_WS_17.001 <- read.csv("./data/csvs/July2025/July2025_17.001_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_17.002 <- read.csv("./data/csvs/July2025/July2025_17.002_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_17.003 <- read.csv("./data/csvs/July2025/July2025_17.003_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_17.004 <- read.csv("./data/csvs/July2025/July2025_17.004_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_17.005 <- read.csv("./data/csvs/July2025/July2025_17.005_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS_17.006 <- read.csv("./data/csvs/July2025/July2025_17.006_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(Latitude, Longitude, treatment, year, tLU_INDEX, cLU_INDEX, Mean_CTRL_W, Mean_t00X_W, delta_W_t00X)
outside_VERTICAL_WS <- bind_rows(outside_VERTICAL_WS_18.001, outside_VERTICAL_WS_18.002, outside_VERTICAL_WS_18.003, outside_VERTICAL_WS_18.004, outside_VERTICAL_WS_18.005, outside_VERTICAL_WS_18.006, outside_VERTICAL_WS_17.001, outside_VERTICAL_WS_17.002, outside_VERTICAL_WS_17.003, outside_VERTICAL_WS_17.004, outside_VERTICAL_WS_17.005, outside_VERTICAL_WS_17.006)


outside <- full_join(outside, outside_ALBEDO_SWDOWN, by = c("Latitude", "Longitude", "treatment", "year", "tLU_INDEX", "cLU_INDEX"))
outside <- full_join(outside, outside_VERTICAL_WS, by = c("Latitude", "Longitude", "treatment", "year", "tLU_INDEX", "cLU_INDEX"))


rm(outside_luc1.17, outside_luc2.17, outside_luc3.17, outside_luc4.17, outside_luc5.17, outside_luc6.17, outside_luc1.18, outside_luc2.18, outside_luc3.18, outside_luc4.18, outside_luc5.18, outside_luc6.18, outside_ALBEDO_SWDOWN_18.001, outside_ALBEDO_SWDOWN_18.002, outside_ALBEDO_SWDOWN_18.003, outside_ALBEDO_SWDOWN_18.004, outside_ALBEDO_SWDOWN_18.005, outside_ALBEDO_SWDOWN_18.006, outside_ALBEDO_SWDOWN_17.001, outside_ALBEDO_SWDOWN_17.002, outside_ALBEDO_SWDOWN_17.003, outside_ALBEDO_SWDOWN_17.004, outside_ALBEDO_SWDOWN_17.005, outside_ALBEDO_SWDOWN_17.006, outside_VERTICAL_WS_18.001, outside_VERTICAL_WS_18.002, outside_VERTICAL_WS_18.003, outside_VERTICAL_WS_18.004, outside_VERTICAL_WS_18.005, outside_VERTICAL_WS_18.006, outside_VERTICAL_WS_17.001, outside_VERTICAL_WS_17.002, outside_VERTICAL_WS_17.003, outside_VERTICAL_WS_17.004, outside_VERTICAL_WS_17.005, outside_VERTICAL_WS_17.006)

## MASKING OUT INTERSTITIAL PIXELS IN SCENARIOS 3 AND 4 ##

mask003 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989))
mask004 <- data.frame(long = c(-80.13846, -80.18411, -81.46793, -82.2084, -82.17819, -80.89255, -80.13846),
                      lat = c(38.33989, 37.74847, 36.83211, 36.85827, 37.4508, 38.37374, 38.33989))
mask003_sf <- st_polygon(list(as.matrix(mask003))) %>% st_sfc(crs = 4326)
mask004_sf <- st_polygon(list(as.matrix(mask004))) %>% st_sfc(crs = 4326)
outside_sf <- st_as_sf(outside, coords = c("Longitude", "Latitude"), crs = 4326)
inside_003 <- st_within(outside_sf, mask003_sf, sparse = FALSE)[,1]
inside_004 <- st_within(outside_sf, mask004_sf, sparse = FALSE)[,1]

keep_point <- case_when(outside_sf$treatment == 3 ~ !inside_003, outside_sf$treatment == 4 ~ !inside_004, TRUE ~ TRUE)
outside_sf <- outside_sf %>% ungroup()
outside_filtered <- outside_sf[keep_point, ] %>% mutate(Longitude = st_coordinates(.)[,1], Latitude = st_coordinates(.)[,2]) %>% st_drop_geometry() %>% filter(delta_VT_t00X <= 1, delta_VT_t00X >= -1) %>% filter(Mean_CTRL_PSN > 2) %>% filter(Mean_t00X_PSN > 2)

rm(mask003, mask003_sf, mask004, mask004_sf, outside_sf)

## MAKING DISTANCE TO DEFORESTATION COLUMN ##
lu_coords <- sprintf("./data/csvs/lat_lons/17_%03d_lat_lon.csv", 1:6)
acsvs_17 <- lapply(lu_coords, read.csv)
csv1 <- acsvs_17[[1]] %>% mutate(t00X_index = row_number(), treatment = 1)
csv2 <- acsvs_17[[2]] %>% mutate(t00X_index = row_number(), treatment = 2)
csv3 <- acsvs_17[[3]] %>% mutate(t00X_index = row_number(), treatment = 3)
csv4 <- acsvs_17[[4]] %>% mutate(t00X_index = row_number(), treatment = 4)
csv5 <- acsvs_17[[5]] %>% mutate(t00X_index = row_number(), treatment = 5)
csv6 <- acsvs_17[[6]] %>% mutate(t00X_index = row_number(), treatment = 6)
lu_16_t001 <- csv1 %>% filter(LU_INDEX == 16) %>% filter(!(t00X_index == 2390)) %>% select(Longitude, Latitude)
lu_16_t002 <- csv2 %>% filter(LU_INDEX == 16) %>% filter(!(t00X_index == 2381)) %>% select(Longitude, Latitude)
lu_16_t003 <- csv3 %>% filter(LU_INDEX == 16) %>% filter(!(t00X_index == 2379)) %>% select(Longitude, Latitude)
lu_16_t004 <- csv4 %>% filter(LU_INDEX == 16) %>% filter(!(t00X_index == 2381)) %>% select(Longitude, Latitude)
lu_16_t005 <- csv5 %>% filter(LU_INDEX == 16) %>% select(Longitude, Latitude)
lu_16_t006 <- csv6 %>% filter(LU_INDEX == 16) %>% filter(!(t00X_index == 2389)) %>% select(Longitude, Latitude)
csv1$distance_to_LU16_meters <- apply(csv1[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t001))})
csv2$distance_to_LU16_meters <- apply(csv2[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t002))})
csv3$distance_to_LU16_meters <- apply(csv3[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t003))})
csv4$distance_to_LU16_meters <- apply(csv4[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t004))})
csv5$distance_to_LU16_meters <- apply(csv5[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t005))})
csv6$distance_to_LU16_meters <- apply(csv6[, c("Longitude", "Latitude")], 1, function(coord) {
  min(distHaversine(coord, lu_16_t006))})
distance_csvs <- bind_rows(csv1, csv2, csv3, csv4, csv5, csv6)
distance_csvs <- distance_csvs %>% filter(LU_INDEX == 4) %>% select(-LU_INDEX, -t00X_index)
outside_filtered <- full_join(outside_filtered, distance_csvs, by = c("Latitude", "Longitude", "treatment"))
outside_filtered <- outside_filtered %>% filter(!is.na(X)) %>% mutate(distance_to_LU16_km = distance_to_LU16_meters / 1000)
rm(acsvs_17, csv1, csv2, csv3, csv4, csv5, csv6, lu_16_t001, lu_16_t002, lu_16_t003, lu_16_t004, lu_16_t005, lu_16_t006, distance_csvs)

## MAKING THETA BUCKETS ##
calculate_polar <- function(lat, lon) {
  r <- distHaversine(c(-81.21869, 37.57799), c(lon, lat))
  theta <- atan2(lat - 37.57799, lon - -81.21869)
  return(c(r, theta))}
outside_filtered <- outside_filtered %>% rowwise() %>%
  mutate(polar = list(calculate_polar(Latitude, Longitude)),
         r = polar[1],
         theta = polar[2]) %>%
  select(-polar) %>% ungroup()
outside_filtered <- outside_filtered %>% mutate(theta_bucket = case_when(theta >= 0 & theta < pi/4 ~ "bucket1",
                                                           theta >= pi/4 & theta < pi/2 ~ "bucket2",
                                                           theta >= pi/2 & theta < 3*pi/4 ~ "bucket3",
                                                           theta >= 3*pi/4 & theta <= pi ~ "bucket4",
                                                           theta < -3*pi/4 & theta >= -pi ~ "bucket5",
                                                           theta < -pi/2 & theta >= -3*pi/4 ~ "bucket6",
                                                           theta < -pi/4 & theta >= -pi/2 ~ "bucket7",
                                                           theta < 0 & theta >= -pi/4 ~ "bucket8"))

## CREATING NORM() REGRESSIONS
outside_filtered <- outside_filtered %>% mutate(normalized_ctrl_GPP = Mean_CTRL_PSN / mean(Mean_CTRL_PSN, na.rm = TRUE) - 1,
                                                normalized_ctrl_APAR = Mean_CTRL_APAR / mean(Mean_CTRL_APAR, na.rm = TRUE) - 1,
                                                normalized_ctrl_SM = Mean_CTRL_SMOIS / mean(Mean_CTRL_SMOIS) - 1,
                                                normalized_ctrl_VPD = Mean_CTRL_VPD / mean(Mean_CTRL_VPD, na.rm = TRUE) - 1,
                                                normalized_ctrl_VT = Mean_CTRL_VT / mean(Mean_CTRL_VT, na.rm = TRUE) - 1)
```


## Import CSVs with complete CTRL data

```{r import_data}
ctrl_17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.001_all_points.csv") %>% filter(Mean_CTRL_PSN > 2)
ctrl_18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.001_all_points.csv") %>% filter(Mean_CTRL_PSN > 2)
```


===========================================================




######### PLOTS #########

## New Figure 1)

```{r}
selected_states2 <- states %>% 
  filter(NAME %in% c("Ohio", "Kentucky", "North Carolina", "Virginia", "West Virginia", "Tennessee","Michigan","Wisconsin","Pennsylvania",
                     "Iowa","Illinois","Missouri","Indiana","Minnesota","Maryland","New York","Arkansas","Louisiana",
                     "South Carolina","Georgia","Mississippi","Alabama","Florida","Delaware","New Jersey"))
clipped_physiographic2 <- st_intersection(physiographic, selected_states2)
syn_box_coords <- data.frame(long = c(-92.953, -74.427, -76.228, -91.634, -92.953),
                             lat = c(43.556, 43.191, 29.951, 30.264, 43.556))
inside_regions2 <- st_intersection(clipped_physiographic2, box_polygon)
outside_regions2 <- st_difference(clipped_physiographic2, box_polygon)
syn_box_polygon <- st_polygon(list(cbind(syn_box_coords$long, syn_box_coords$lat))) %>% 
  st_sfc(crs = st_crs(clipped_physiographic2))
inside_syn_regions <- st_intersection(clipped_physiographic2, syn_box_polygon)
outside_syn_regions <- st_difference(clipped_physiographic2, syn_box_polygon)
outside_regions2 <- st_difference(outside_syn_regions, box_polygon)
inside_syn_colors <- colorRampPalette(brewer.pal(9, "Blues"))(length(unique(inside_syn_regions$PROVINCE)))
inside_colors2 <- colorRampPalette(brewer.pal(4, "Greens"))(length(unique(inside_regions2$PROVINCE)))
outside_colors2 <- colorRampPalette(brewer.pal(9, "Reds"))(length(unique(outside_regions2$PROVINCE)))
inside_palette2 <- setNames(inside_colors2, unique(inside_regions2$PROVINCE))
inside_syn_palette <- setNames(inside_syn_colors, unique(inside_syn_regions$PROVINCE))
outside_palette2 <- setNames(outside_colors2, unique(outside_regions2$PROVINCE))
inside_syn_regions <- inside_syn_regions %>% mutate(color = inside_syn_palette[PROVINCE]) %>%
  group_by(color) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
inside_regions2 <- inside_regions2 %>% mutate(color = inside_palette2[PROVINCE]) %>%
  group_by(color) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
outside_regions2 <- outside_regions2 %>% mutate(color = "lightgrey") %>%
  group_by(color) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
combined_regions2 <- bind_rows(inside_syn_regions, inside_regions2, outside_regions2)
selected_states2 <- st_transform(selected_states2, crs = 4326)
combined_regions2 <- st_transform(combined_regions2, crs = 4326)
syn_box_polygon <- st_transform(syn_box_polygon, crs = 4326)
syn_box_df <- st_as_sf(syn_box_polygon)
create_great_circle <- function(lon1, lat1, lon2, lat2) {
  gc <- gcIntermediate(c(lon1, lat1), c(lon2, lat2), n=100, addStartEnd=TRUE, sp=TRUE)
  return(gc)
}
great_circle_lines <- lapply(1:(nrow(syn_box_coords) - 1), function(i) {
  create_great_circle(syn_box_coords$long[i], syn_box_coords$lat[i], syn_box_coords$long[i+1], syn_box_coords$lat[i+1])
})
great_circle_sf <- do.call(rbind, lapply(great_circle_lines, st_as_sf))
green_great_circle_lines <- lapply(1:(nrow(box_coords) - 1), function(i) {
  create_great_circle(box_coords$long[i], box_coords$lat[i], box_coords$long[i+1], box_coords$lat[i+1])
})
green_great_circle_sf <- do.call(rbind, lapply(green_great_circle_lines, st_as_sf))
SynopticDomainMap <- ggplot() +
  geom_sf(data = combined_regions2, aes(fill = color), color = "black", linewidth = 0, alpha = 1) +
  scale_fill_identity(name = "Physiographic Regions", 
                      breaks = c(inside_palette2, inside_syn_palette), 
                      labels = c(names(inside_palette2), names(inside_syn_palette)), 
                      guide = "legend") +
  geom_sf(data = great_circle_sf, color = "darkblue", alpha = 0.5, linewidth = 1.5) +
  geom_sf(data = green_great_circle_sf, color = "darkgreen", alpha = 0.5, linewidth = 1.5) +
  geom_sf(data = selected_states2, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-90, -80)) +
  scale_y_continuous(breaks = c(30, 45)) +
  theme_test() +
  labs(title = "Parent & Focal Domain") +
  guides(fill = "none") +
  standardized_theme
#rm(clipped_physiographic2, combined_regions2, great_circle_lines, great_circle_sf, green_great_circle_lines, green_great_circle_sf, inside_regions2, inside_syn_regions, outside_regions2, outside_syn_regions, selected_states2, syn_box_coords, syn_box_df, syn_box_polygon, inside_colors2, inside_palette2, inside_syn_colors, inside_syn_palette, outside_colors2, create_great_circle, outside_palette2)

nc_whatever_for_landuse <- nc_open("./data/netCDF_files/wrfout_2017_control_domain.nc")
lat <- ncvar_get(nc_whatever_for_landuse, "XLAT")
lon <- ncvar_get(nc_whatever_for_landuse, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lat)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_whatever_for_landuse, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
elevation <- matrix(0, nrow = dim(lat)[1], ncol = dim(lat)[2])
for (i in 1:100) {
  for (j in 1:100) {
    elevation[i, j] <- ncvar_get(nc_whatever_for_landuse, "HGT", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
soil_type <- matrix(0, nrow = dim(lat)[1], ncol = dim(lat)[2])
for (i in 1:100) {
  for (j in 1:100) {
    soil_type[i, j] <- ncvar_get(nc_whatever_for_landuse, "ISLTYP", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
full_table <- data.frame(
  lon = as.vector(lon),
  lat = as.vector(lat),
  LU_INDEX = as.vector(landuse),
  ELEVATION = as.vector(elevation),
  SOIL_TYPE = as.vector(soil_type))
nc_close(nc_whatever_for_landuse)
#rm(lat, lon, landuse, elevation, soil_type)
full_table <- full_table %>%
  mutate(SOIL_TYPE = ifelse(SOIL_TYPE %in% c(2,8,11,14,16), 1, SOIL_TYPE)) %>% 
  mutate(SOIL_TYPE = recode(SOIL_TYPE, '1' = "Other", '3' = "Sandy Loam", '4' = "Silt Loam", '6' = "Loam")) %>% 
  mutate(LU_INDEX = ifelse(LU_INDEX %in% c(2,3,5), 1, LU_INDEX)) %>% 
  mutate(LU_INDEX = ifelse(LU_INDEX %in% c(7,8,9,10,11,12,13,14,15,17), 6, LU_INDEX)) %>% 
  mutate(LU_INDEX = recode(LU_INDEX, '1' = "Different Forest Types", '4' = "Deciduous Broadleaf Forest", '6' = "Other LU Types", '16' = "Barren or Sparsely Vegetated"))
prop.table(table(full_table$LU_INDEX))
prop.table(table(full_table$SOIL_TYPE))
MODISpoints <- data.frame(
  lat = c(36.45, 36.45, 36.79, 36.70, 36.5, 36.7, 36.9, 37.18, 37, 38, 37.5, 38.62, 38.25, 37.75, 38.5, 38.25, 37.55, 38.65, 37.378314),
  lon = c(-80.00, -80.76, -80.00, -80.27, -81.75, -81.15, -80.5, -80, -81.5, -80, -82.5, -82.35, -82, -81.5, -81.25, -80.5, -80.65, -80, -80.524847))

land_use <- ggplot() +
  geom_point(data = full_table, aes(x = lon, y = lat, color = LU_INDEX), shape = 15, size = 0.85) +
  scale_color_manual(values = c("Different Forest Types" = "#4361EE",
                                "Deciduous Broadleaf Forest" = "#80ED99",
                                "Other LU Types" = "#F28482", 
                                "Barren or Sparsely Vegetated" = "black"), name = NULL) +
  geom_point(data = MODISpoints, aes(x = lon, y = lat, shape = "MODIS Validation Sites"), fill = "white", color = "black", size = 1.7) +
  scale_shape_manual(values = c("MODIS Validation Sites" = 21)) +
  guides(shape = guide_legend(title = NULL, override.aes = list(size = 5))) +
  geom_sf(data = combined_regions, color = "black", linewidth = 0.1, alpha = 0) + 
  geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  theme_test() +
  labs(x = NULL, y = NULL, title = "Land Use") +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  standardized_theme +
  theme(legend.position = "bottom", legend.key.size = unit(0.4, "cm"), 
  legend.text = element_text(size = 8)) +
  guides(color = guide_legend(nrow = 4, override.aes = list(size = 5)))
elevation <- ggplot() +
  geom_point(data = full_table, aes(x = lon, y = lat, color = ELEVATION), shape = 15, size = 0.85) +
  scale_color_scico(palette = "oslo", name = expression("Elev. (m)")) +
  geom_sf(data = combined_regions, color = "red", linewidth = 0.5, alpha = 0) + 
  geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  theme_test() +
  labs(x = NULL, y = NULL, title = "Elevation") +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  standardized_theme +
  theme(legend.position = "bottom", legend.key.size = unit(0.4, "cm"),
  legend.text = element_text(size = 8))
soil_type <- ggplot() +
  geom_point(data = full_table, aes(x = lon, y = lat, color = SOIL_TYPE), shape = 15, size = 0.85) +
  scale_color_manual(values = c("Sandy Loam" = "#EFC457",
                                "Silt Loam" = "#98710F",
                                "Loam" = "#653D01", 
                                "Other" = "purple"), name = NULL) +
  geom_sf(data = combined_regions, color = "black", linewidth = 0.1, alpha = 0) + 
  geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  theme_test() +
  labs(x = NULL, y = NULL, title = "Soil Types") +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme(legend.position = "bottom", legend.key.size = unit(0.4, "cm"), legend.text = element_text(size = 8), plot.title = element_text(hjust = 0.5, face="bold")) +
  guides(color = guide_legend(nrow = 1, override.aes = list(size = 5)))

#figs_234 <- ggarrange(elevation, soil_type, land_use, nrow = 1, ncol = 3, align = "hv")


fig_1 <- ggarrange(SynopticDomainMap, land_use, elevation, soil_type, nrow = 2, ncol = 2, labels = c("(A)", "(B)", "(C)", "(D)"))
ggsave("~/Desktop/fig_1.pdf", fig_1, width = 9.5, height = 9.5, units = "in")


#ggsave("2figs_234.pdf", figs_234, width = 15, height = 7, units = "in")
#rm(lat, lon, landuse, land_use, MODISpoints, elevation, full_table, nc_whatever_for_landuse, soil_type)
```


## New Figure 2)

```{r}
PCO2 <- 39.5     ## CO2 in Pa (39.5 Pa = 395 ppm from MP table)
Psfc <- 100000   ## Surface air pressure in Pa (100000 Pa = 1 atm)
C3psn <- 1.0     ## C3 photosynthesis (1.0 for C3, 0.0 for C4)
PO2 <- 20900     ## Oxygen partial pressure in Pa (from MP table)
KC25 <- 30.0       ## Michaelis constant for CO2 at 25°C in Pa (from MP table)
KC10 <- 2.1        ## Michaelis Q10 for CO2 (from MP table)
KO25 <- 30000      ## Michaelis constant for O2 at 25°C in Pa (from MP table)
KO10 <- 1.2        ## Michaelis Q10 for O2 (from MP table)
temp_range <- seq(0, 50, by = 1)  ## From 0 to 50°C... shouldn't be any warmer than that.
Sppf <- 4.6 * 1:3 *40 ## as high as 280, but for illustrative purposes, 120 W/m^2 is as high as we need to go
QE25 <- 0.060      
Beta_sm<-1:3/3 ## ranges from no moisture stress to 1/3 to 2/3 of maximum moisture stress

##################################
####### Light Limited Rate #######
##################################

light_limited <- function(Je, PCO2init, PcCO2, C3psn) {
  ((max(PCO2init - PcCO2, 0) * Je) / (PCO2init + 2*PcCO2)) * C3psn + Je * (1 - C3psn)}

light_limited_values <- numeric(length(temp_range))

light_limited_df_old <- data.frame(Temp = temp_range)
light_limited_df_new <- data.frame(Temp = temp_range)

for(h in 1:length(Sppf)){
  for (i in 1:length(temp_range)) {
    Je <- Sppf[h] * QE25
    Temp <- temp_range[i]
    KC <- KC25 * KC10^((Temp - 25) / 10)
    KO <- KO25 * KO10^((Temp - 25) / 10)
    PcCO2 <- 0.5 * (KC / KO) * PO2 * 0.21
    PCO2init <- 0.7 * PCO2 * C3psn + 0.4 * PCO2 * (1 - C3psn)
    light_limited_values[i] <- light_limited(Je, PCO2init, PcCO2, C3psn)}
  light_limited_df_old[[paste0("LIGHT_",Sppf[h]/4.6)]] <- light_limited_values
  light_limited_df_new[[paste0("LIGHT_",Sppf[h]/4.6)]] <- light_limited_values
}

#light_limited_df_old <- light_limited_df %>% pivot_longer(cols = c("40", "80", "120"), names_to = "Light", values_to = "Light_Limitation") %>% mutate(params = "old")
#light_limited_df_new <- light_limited_df %>% pivot_longer(cols = c("40", "80", "120"), names_to = "Light", values_to = "Light_Limitation") %>% mutate(params = "new")

light_limited_df_old <- light_limited_df_old %>% mutate(params = "old")
light_limited_df_new <- light_limited_df_new %>% mutate(params = "new")


light_limited_df <- full_join(light_limited_df_old, light_limited_df_new, by = c("Temp", "params", "LIGHT_40", "LIGHT_80", "LIGHT_120"))


## ORIGINAL PARAMETERS ##
old_Vcmax25 <- 60
old_Vcmax10 <- 2.4
new_Vcmax25 <- 43
new_Vcmax10 <- 3.4


####################################
##### Rubisco Limited Rate #####
####################################

rub_limited <- function(Vcmax, PCO2init, PcCO2, Fwc, C3psn) {
  ((max(PCO2init - PcCO2, 0) * Vcmax) / (PCO2init + Fwc)) * C3psn + Vcmax * (1 - C3psn)}

old_rub_limited_values <- numeric(length(temp_range))
new_rub_limited_values <- numeric(length(temp_range))

old_rub_limited_df <- data.frame(Temp = temp_range)
new_rub_limited_df <- data.frame(Temp = temp_range)

for(h in 1:length(Beta_sm)){
  
  for (i in 1:length(temp_range)) {
    Temp <- temp_range[i]
    KC <- KC25 * KC10^((Temp - 25) / 10)
    KO <- KO25 * KO10^((Temp - 25) / 10)
    PcCO2 <- 0.5 * (KC / KO) * PO2 * 0.21
    PCO2init <- 0.7 * PCO2 * C3psn + 0.4 * PCO2 * (1 - C3psn)
    Fwc <- KC * (1 + (PO2 / KO))
    old_Vcmax <- old_Vcmax25 * 1 * Beta_sm[h] * ((old_Vcmax10^((Temp - 25) / 10)) / (1 + exp((-2.2 * 10^5 + 710 * (Temp + 273.16)) / (8.314 * (Temp + 273.16)))))
    new_Vcmax <- new_Vcmax25 * 1 * Beta_sm[h] * ((new_Vcmax10^((Temp - 25) / 10)) / (1 + exp((-2.2 * 10^5 + 710 * (Temp + 273.16)) / (8.314 * (Temp + 273.16)))))
    old_rub_limited_values[i] <- rub_limited(old_Vcmax, PCO2init, PcCO2, Fwc, C3psn)
    new_rub_limited_values[i] <- rub_limited(new_Vcmax, PCO2init, PcCO2, Fwc, C3psn)}
  old_rub_limited_df[[paste0("RUB_SM_",round(Beta_sm[h],2))]] <- old_rub_limited_values
  new_rub_limited_df[[paste0("RUB_SM_",round(Beta_sm[h],2))]] <- new_rub_limited_values
}

#old_rub_limited_df <- old_rub_limited_df %>% pivot_longer(cols = c("0.33", "0.67", "1"), names_to = "Beta_sm", values_to = "Rub_Limitation") %>% mutate(params = "old")
#new_rub_limited_df <- new_rub_limited_df %>% pivot_longer(cols = c("0.33", "0.67", "1"), names_to = "Beta_sm", values_to = "Rub_Limitation") %>% mutate(params = "new")

old_rub_limited_df <- old_rub_limited_df %>% mutate(params = "old")
new_rub_limited_df <- new_rub_limited_df %>% mutate(params = "new")


rub_limited_df <- full_join(old_rub_limited_df, new_rub_limited_df, by = c("Temp", "params", "RUB_SM_0.33", "RUB_SM_0.67", "RUB_SM_1"))


###################################
##### Export Limited Rate #####
###################################
old_exp_limited_values <- numeric(length(temp_range))
new_exp_limited_values <- numeric(length(temp_range))
old_exp_limited_df <- data.frame(Temp = temp_range)
new_exp_limited_df <- data.frame(Temp = temp_range)

export_limited <- function(Vcmax, PCO2init, Psfc, C3psn) {
  0.5 * Vcmax * C3psn + 4000 * Vcmax * (PCO2init/Psfc) * (1-C3psn)}

for(h in 1:length(Beta_sm)){
  
  for (i in 1:length(temp_range)) {
    Temp <- temp_range[i]
    KC <- KC25 * KC10^((Temp - 25) / 10)
    KO <- KO25 * KO10^((Temp - 25) / 10)
    PcCO2 <- 0.5 * (KC / KO) * PO2 * 0.21
    PCO2init <- 0.7 * PCO2 * C3psn + 0.4 * PCO2 * (1 - C3psn)
    Fwc <- KC * (1 + (PO2 / KO))
    old_Vcmax <- old_Vcmax25 * Beta_sm[h] * 0.9 * ((old_Vcmax10^((Temp - 25) / 10)) / (1 + exp((-2.2 * 10^5 + 710 * (Temp + 273.16)) / (8.314 * (Temp + 273.16)))))
    new_Vcmax <- new_Vcmax25 * Beta_sm[h] * 0.9 * ((new_Vcmax10^((Temp - 25) / 10)) / (1 + exp((-2.2 * 10^5 + 710 * (Temp + 273.16)) / (8.314 * (Temp + 273.16)))))
    old_exp_limited_values[i] <- export_limited(old_Vcmax, PCO2init, Psfc, C3psn)
    new_exp_limited_values[i] <- export_limited(new_Vcmax, PCO2init, Psfc, C3psn)}
  old_exp_limited_df[[paste0("EXP_SM_",round(Beta_sm[h],2))]] <- old_exp_limited_values
  new_exp_limited_df[[paste0("EXP_SM_",round(Beta_sm[h],2))]] <- new_exp_limited_values
}

#old_exp_limited_df <- old_exp_limited_df %>% pivot_longer(cols = c("0.33", "0.67", "1"), names_to = "Beta_sm", values_to = "Exp_Limitation") %>% mutate(params = "old")
#new_exp_limited_df <- new_exp_limited_df %>% pivot_longer(cols = c("0.33", "0.67", "1"), names_to = "Beta_sm", values_to = "Exp_Limitation") %>% mutate(params = "new")

old_exp_limited_df <- old_exp_limited_df %>% mutate(params = "old")
new_exp_limited_df <- new_exp_limited_df %>% mutate(params = "new")

exp_limited_df <- full_join(old_exp_limited_df, new_exp_limited_df, by = c("Temp", "params", "EXP_SM_0.33", "EXP_SM_0.67", "EXP_SM_1"))

photosynthetic_rate_df <- left_join(rub_limited_df, exp_limited_df, by = c("Temp", "params"))
photosynthetic_rate_df <- left_join(photosynthetic_rate_df, light_limited_df, by = c("Temp", "params"))

photosynthetic_rate_df2 <- photosynthetic_rate_df %>% pivot_longer(cols = c(RUB_SM_0.33, RUB_SM_0.67, RUB_SM_1), names_to = "SM_rubisco", values_to = "Rubisco_Limited") %>%
  pivot_longer(cols = c(EXP_SM_0.33, EXP_SM_0.67, EXP_SM_1), names_to = "SM_export", values_to = "Export_Limited") %>%
  pivot_longer(cols = c(LIGHT_40, LIGHT_80, LIGHT_120), names_to = "LIGHT", values_to = "Light_Limited") %>%
  mutate(LIGHT = ifelse(LIGHT == "LIGHT_120", 120, LIGHT), LIGHT = ifelse(LIGHT == "LIGHT_80", 80, LIGHT), LIGHT = ifelse(LIGHT == "LIGHT_40", 40, LIGHT),
         SM_rubisco = ifelse(SM_rubisco == "RUB_SM_0.33", "2/3", SM_rubisco), SM_rubisco = ifelse(SM_rubisco == "RUB_SM_0.67", "1/3", SM_rubisco), SM_rubisco = ifelse(SM_rubisco == "RUB_SM_1", 0, SM_rubisco),
         SM_export = ifelse(SM_export == "EXP_SM_0.33", "2/3", SM_export), SM_export = ifelse(SM_export == "EXP_SM_0.67", "1/3", SM_export), SM_export = ifelse(SM_export == "EXP_SM_1", 0, SM_export),
         params = ifelse(params == "old", "Old Params", params), params = ifelse(params == "new", "New Params", params))

#18.785523 18.8
#13.462958 13.5

old_x_segment <- data.frame(x = c(0, 25), y = c(18.785523, 18.785523), params = "Old Params")
old_y_segment <- data.frame(x = c(25, 25), y = c(0, 18.785523), params = "Old Params")
old_point <- data.frame(x = 25, y = 18.785523, params = "Old Params")

new_x_segment <- data.frame(x = c(0, 25), y = c(13.462958, 13.462958), params = "New Params")
new_y_segment <- data.frame(x = c(25, 25), y = c(0, 13.462958), params = "New Params")
new_point <- data.frame(x = 25, y = 13.462958, params = "New Params")

photosynthetic_rate_df2 <- photosynthetic_rate_df2 %>% mutate(LIGHT = factor(LIGHT, levels = c(40, 80, 120)), params = factor(params, levels = c("Old Params", "New Params")))

#rm(exp_limited_df, light_limited_df, light_limited_df_new, light_limited_df_old, new_exp_limited_df, new_rub_limited_df, old_exp_limited_df, old_rub_limited_df, photosynthetic_rate_df, rub_limited_df, Beta_sm, C3psn, Fwc, h, i, Je, KC, KC10, KC25, KO, KO10, KO25, light_limited_values, lty_values, lwd_values, new_exp_limited_values, new_rub_limited_values, new_Vcmax, new_Vcmax10, new_Vcmax25, old_exp_limited_values, old_rub_limited_values, old_Vcmax, old_Vcmax10, old_Vcmax25, PcCO2, PCO2, PCO2init, PO2, Psfc, QE25, Sppf, Temp, temp_range, export_limited, light_limited, rub_limited)

plots1and2 <- ggplot(data = photosynthetic_rate_df2) +
  geom_line(aes(x = Temp, y = Light_Limited, linewidth = LIGHT, color = "Light")) +
  geom_line(aes(x = Temp, y = Export_Limited, linetype = SM_export, color = "Export"), linewidth = 1.5) +
  geom_line(aes(x = Temp, y = Rubisco_Limited, linetype = SM_rubisco, color = "Rubisco"), linewidth = 1.5) +
  geom_line(data = old_x_segment, aes(x = x, y = y)) +
  geom_line(data = old_y_segment, aes(x = x, y = y)) +
  geom_point(data = old_point, aes(x = x, y = y), size = 3.5, color = "purple") +
  geom_line(data = new_x_segment, aes(x = x, y = y)) +
  geom_line(data = new_y_segment, aes(x = x, y = y)) +
  geom_point(data = new_point, aes(x = x, y = y), size = 3.5, color = "purple") +
  scale_linetype_manual(values = c("2/3" = "dotted", "1/3" = "twodash", "0" = "solid")) +
  scale_linewidth_manual(values = c("40" = 1.5, "80" = 3, "120" = 4.5)) +
  facet_grid(~params) +
  theme_bw() +
  labs(color = "Limiting Process:", linewidth = expression("Light Intensity (W m"^{-2} * "):"), linetype = expression("SM Stress:"), x = "Temperature (°C)", y = expression(mu * "mol CO"[2] * " m"^{-2} * " s"^{-1})) +
  theme(legend.position = "bottom", legend.text = element_text(size = 14), legend.title = element_text(size = 14), axis.title = element_text(size = 14), axis.text = element_text(size = 14), strip.text = element_text(size = 16)) +
  guides(color = guide_legend(nrow = 2), linewidth = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2))

###########

modis_gpp_list <- list()
model.out.of.the.box.gpp.list <- list()
model.adjusted.params.gpp.list <- list()

start_date_2017 <- as.POSIXct("2017-01-01", tz = "UTC")
start_date_2018 <- as.POSIXct("2018-01-01", tz = "UTC")

for (i in 1:19) {
  modis_file <- sprintf("./data/gpp_validation/modis_point_%03d.csv", i)
  model.out.of.the.box.file <- sprintf("./data/gpp_validation/pre_validation_%03d.csv", i)
  model.adjusted.params.file <- sprintf("./data/gpp_validation/validation%03d.csv", i)
  modis_data <- read.csv(modis_file) %>% dplyr::select(calendar_date, value) %>% mutate(calendar_date = as.Date(calendar_date), GPP_MODIS = value * 1e-4) %>%
    group_by(calendar_date) %>% summarise(!!paste0("average_gpp_", sprintf("%03d", i)) := mean(GPP_MODIS, na.rm = TRUE), .groups = "drop") %>%
    mutate(time = as.POSIXct(calendar_date, format="%Y-%m-%d", tz="UTC")) %>% dplyr::select(-calendar_date)
  model.out.of.the.box <- read.csv(model.out.of.the.box.file) %>% mutate(fixtimes = as.POSIXct(DateTime, format="%Y-%m-%dT%H:%M:%SZ", tz="UTC"), GPP_model_1_kg_per_s = GPP * 1e-3)
  model.out.of.the.box.2017.8day <- model.out.of.the.box %>% 
    filter(fixtimes < as.POSIXct("2018-01-01", tz = "UTC")) %>%
    mutate(time = start_date_2017 + floor(as.numeric(difftime(fixtimes, start_date_2017, units = "days")) / 8) * 8 * 86400) %>%
    group_by(time) %>%
    summarize(!!paste0("Model_1_kg_per_8days_", sprintf("%03d", i)) := sum(GPP_model_1_kg_per_s * 3600, na.rm = TRUE), .groups = "drop")
  model.out.of.the.box.2018.8day <- model.out.of.the.box %>% 
    filter(fixtimes >= as.POSIXct("2018-01-01", tz = "UTC")) %>%
    mutate(time = start_date_2018 + floor(as.numeric(difftime(fixtimes, start_date_2018, units = "days")) / 8) * 8 * 86400) %>%
    group_by(time) %>%
    summarize(!!paste0("Model_1_kg_per_8days_", sprintf("%03d", i)) := sum(GPP_model_1_kg_per_s * 3600, na.rm = TRUE), .groups = "drop")
  model.adjusted.params <- read.csv(model.adjusted.params.file) %>% mutate(fixtimes = as.POSIXct(DateTime, format="%Y-%m-%dT%H:%M:%SZ", tz="UTC"), GPP_model_2_kg_per_s = GPP * 1e-3)
  model.adjusted.params.2017.8day <- model.adjusted.params %>%
    filter(fixtimes < as.POSIXct("2018-01-01", tz = "UTC")) %>%
    mutate(time = start_date_2017 + floor(as.numeric(difftime(fixtimes, start_date_2017, units = "days")) / 8) * 8 * 86400) %>%
    group_by(time) %>%
    summarize(!!paste0("Model_2_kg_per_8days_", sprintf("%03d", i)) := sum(GPP_model_2_kg_per_s * 3600, na.rm = TRUE), .groups = "drop")
  model.adjusted.params.2018.8day <- model.adjusted.params %>% 
    filter(fixtimes >= as.POSIXct("2018-01-01", tz = "UTC")) %>%
    mutate(time = start_date_2018 + floor(as.numeric(difftime(fixtimes, start_date_2018, units = "days")) / 8) * 8 * 86400) %>%
    group_by(time) %>%
    summarize(!!paste0("Model_2_kg_per_8days_", sprintf("%03d", i)) := sum(GPP_model_2_kg_per_s * 3600, na.rm = TRUE), .groups = "drop")
  modis_gpp_list[[i]] <- modis_data
  model.out.of.the.box.gpp.list[[i]] <- bind_rows(model.out.of.the.box.2017.8day, model.out.of.the.box.2018.8day)
  model.adjusted.params.gpp.list[[i]] <- bind_rows(model.adjusted.params.2017.8day, model.adjusted.params.2018.8day)
}
modis_data_all <- Reduce(function(x, y) merge(x, y, by = "time", all = TRUE), modis_gpp_list)
model.out.of.the.box.data.all <- Reduce(function(x, y) merge(x, y, by = "time", all = TRUE), model.out.of.the.box.gpp.list)
model.adjusted.params.data.all <- Reduce(function(x, y) merge(x, y, by = "time", all = TRUE), model.adjusted.params.gpp.list)
merged_data <- left_join(modis_data_all, model.out.of.the.box.data.all, by = "time")
merged_data <- left_join(merged_data, model.adjusted.params.data.all, by = "time")
average_modis_gpp <- merged_data %>%
  pivot_longer(cols = starts_with("average_gpp_"), names_to = "variable", values_to = "gpp_value") %>%
  group_by(time) %>%
  summarise(average_modis_gpp = mean(gpp_value, na.rm = TRUE), .groups = "drop")
average_modeled_gpp_1 <- merged_data %>%
  pivot_longer(cols = starts_with("Model_1_kg_per_8days_"),names_to = "variable", values_to = "gpp_value") %>%
  group_by(time) %>%
  summarise(average_modeled_gpp_1 = mean(gpp_value, na.rm = TRUE), .groups = "drop")
average_modeled_gpp_2 <- merged_data %>%
  pivot_longer(cols = starts_with("Model_2_kg_per_8days_"),names_to = "variable", values_to = "gpp_value") %>%
  group_by(time) %>%
  summarise(average_modeled_gpp_2 = mean(gpp_value, na.rm = TRUE), .groups = "drop")
final_data <- merged_data %>%
  left_join(average_modis_gpp, by = "time") %>%
  left_join(average_modeled_gpp_1, by = "time") %>%
  left_join(average_modeled_gpp_2, by = "time") %>%
  mutate(time = as.Date(time))
final_data <- na.omit(final_data)
final_data2 <- final_data %>% select(time, average_modis_gpp, average_modeled_gpp_1, average_modeled_gpp_2) %>% filter(time >= "2017-01-17", !time == "2018-11-01")
## Jan 1 & 9 were removed as an initialization period.
## NOTE FOR FUTURE PEOPLES: MODIS data, and the model data, collapse *down*. Meaning, for instance, October 24th contains data running from the 24th through the 31st. This is why the November 1st point was removed, as it was binning all of one hour (00:00:00), which was 0.
sum(final_data2$average_modis_gpp)
sum(final_data2$average_modeled_gpp_1)
sum(final_data2$average_modeled_gpp_2)

(sum(final_data2$average_modeled_gpp_1) - sum(final_data2$average_modis_gpp))/sum(final_data2$average_modis_gpp)

(sum(final_data2$average_modeled_gpp_2) - sum(final_data2$average_modis_gpp))/sum(final_data2$average_modis_gpp)

time_plot3 <- ggplot(final_data2) +
  geom_line(aes(x = time, y = average_modis_gpp, color = "MODIS"), linewidth = 0.65) +
  geom_line(aes(x = time, y = average_modeled_gpp_1, color = "Initial Param."), linewidth = 0.65) +
  geom_line(aes(x = time, y = average_modeled_gpp_2, color = "Modified Param."), linewidth = 0.65) +
  labs(x = NULL, y = expression("GPP " * "(" * kg ~ C ~ m^{-2} * " per 8 days" * ")"), title = "Impact on Model GPP") +
  scale_color_manual(values = c("MODIS" = "skyblue", "Initial Param." = "tomato", "Modified Param." = "forestgreen"), name = "") +
  theme_bw() +
  xlim(as.Date("2017-01-01"), as.Date("2018-11-02")) +
  ylim(0, 0.11) +
  theme(legend.position = "bottom", legend.text = element_text(size = 12), axis.title = element_text(size = 14), axis.text = element_text(size = 14), plot.title = element_text(hjust = 0.5, size = 16))

fig_2_plot_sheet <- ggarrange(plots1and2, time_plot3, widths = c(2,1), labels = c("(A)", "(B)"), font.label = list(size = 16))

ggsave("~/Desktop/fig_2_plot_sheet.pdf", fig_2_plot_sheet, width = 15.5, height = 6.2, units = "in")

##########


```


## New Figure 3)

```{r}
nc_17_001 <- nc_open("./data/netCDF_files/wrfout_2017_t001_domain.nc")
lat <- ncvar_get(nc_17_001, "XLAT")
lon <- ncvar_get(nc_17_001, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_001, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_001)
LU_graphable.1 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 1")

nc_17_002 <- nc_open("./data/netCDF_files/wrfout_2017_t002_domain.nc")
lat <- ncvar_get(nc_17_002, "XLAT")
lon <- ncvar_get(nc_17_002, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_002, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_002)
LU_graphable.2 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 2")

nc_17_003 <- nc_open("./data/netCDF_files/wrfout_2017_t003_domain.nc")
lat <- ncvar_get(nc_17_003, "XLAT")
lon <- ncvar_get(nc_17_003, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_003, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_003)
LU_graphable.3 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 3")

nc_17_004 <- nc_open("./data/netCDF_files/wrfout_2017_t004_domain.nc")
lat <- ncvar_get(nc_17_004, "XLAT")
lon <- ncvar_get(nc_17_004, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_004, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_004)
LU_graphable.4 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 4")


nc_17_005 <- nc_open("./data/netCDF_files/wrfout_2017_t005_domain.nc")
lat <- ncvar_get(nc_17_005, "XLAT")
lon <- ncvar_get(nc_17_005, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_005, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_005)
LU_graphable.5 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 5")

nc_17_006 <- nc_open("./data/netCDF_files/wrfout_2017_t006_domain.nc")
lat <- ncvar_get(nc_17_006, "XLAT")
lon <- ncvar_get(nc_17_006, "XLONG")
landuse <- matrix(0, nrow = dim(lat)[1], ncol = dim(lon)[2])
for (i in 1:100) {
  for (j in 1:100) {
    landuse[i, j] <- ncvar_get(nc_17_006, "LU_INDEX", start = c(i, j, 1), count = c(1, 1, 1))
  }
}
nc_close(nc_17_006)
LU_graphable.6 <- data.frame(lon = as.vector(lon),
                             lat = as.vector(lat),
                             LU_INDEX = as.vector(landuse),
                             Treatment = "Scenario 6")

LU_maps <- bind_rows(LU_graphable.1, LU_graphable.2, LU_graphable.3, LU_graphable.4, LU_graphable.5, LU_graphable.6)
rm(LU_graphable.1, LU_graphable.2, LU_graphable.3, LU_graphable.4, LU_graphable.5, LU_graphable.6)


LU_maps <- LU_maps %>%
  mutate(LU_INDEX = ifelse(LU_INDEX %in% c(2,3,5), 1, LU_INDEX)) %>% 
  mutate(LU_INDEX = ifelse(LU_INDEX %in% c(7,8,9,10,11,12,13,14,15,17), 6, LU_INDEX)) %>% 
  mutate(LU_INDEX = recode(LU_INDEX, '1' = "Different Forest Types", '4' = "Deciduous Broadleaf Forest", '6' = "Other LU Types", '16' = "Barren or Sparsely Vegetated"))

LU_maps_plot <- ggplot() +
  geom_point(data = LU_maps, aes(x = lon, y = lat, color = LU_INDEX), shape = 15, size = 0.33) +
  scale_color_manual(values = c("Different Forest Types" = "#4361EE",
                                "Deciduous Broadleaf Forest" = "#80ED99",
                                "Other LU Types" = "#F28482", 
                                "Barren or Sparsely Vegetated" = "black"), name = NULL) +
  geom_sf(data = combined_regions, color = "purple", linewidth = 0.01, alpha = 0) + 
  geom_sf(data = selected_states, fill = "NA", color = "grey", linewidth = 0.03, alpha = 0.5) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_wrap(~ Treatment, nrow = 1) +
  labs(x = NULL, y = NULL) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "bottom", legend.text = element_text(size = 14), strip.text = element_text(size = 16)) +
  guides(color = guide_legend(override.aes = list(size = 6)))


ggsave("~/Desktop/FIG3_test.pdf", LU_maps_plot, width = 11.25, height = 2.5, units = "in")


```


## New Figure 4)

```{r}
require(data.table)
require(ggnewscale)
require(patchwork)

ctrl_17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.001_all_points.csv") %>% filter(Mean_CTRL_PSN > 2)
ctrl_18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.001_all_points.csv") %>% filter(Mean_CTRL_PSN > 2)

fig_4_df_17 <- ctrl_17 %>% mutate(Year = 2017) %>% select(Latitude, Longitude, Year, Mean_CTRL_VT, Mean_CTRL_SMOIS, Mean_CTRL_APAR, Mean_CTRL_VPD, Mean_CTRL_PSN) %>% reshape2::melt(id.vars = c("Latitude", "Longitude", "Year"), variable.name = "variable", value.name = "value")
fig_4_df_18 <- ctrl_18 %>% mutate(Year = 2018) %>% select(Latitude, Longitude, Year, Mean_CTRL_VT, Mean_CTRL_SMOIS, Mean_CTRL_APAR, Mean_CTRL_VPD, Mean_CTRL_PSN) %>% reshape2::melt(id.vars = c("Latitude", "Longitude", "Year"), variable.name = "variable", value.name = "value")
fig_4_df <- full_join(fig_4_df_17, fig_4_df_18)

fig_4_df <- fig_4_df %>% mutate(variable = recode(variable, 'Mean_CTRL_VT' = "Veg Temp (K)", 'Mean_CTRL_SMOIS' = "SM (m3/m3)", 'Mean_CTRL_APAR' = "APAR (W/m2)", 'Mean_CTRL_VPD' = "VPD (Pa)", 'Mean_CTRL_PSN' = "GPP (umol/m2/s-1)"))


palettes <- c("Veg Temp (K)"        = "roma",
              "SM (m3/m3)"          = "oslo",
              "APAR (W/m2)"         = "lajolla",
              "VPD (Pa)"            = "batlow",
              "GPP (umol/m2/s-1)"   = "tokyo")

legend_labels <- c("Veg Temp (K)"        = "VegTemp",
                   "SM (m3/m3)"          = "SM",
                   "APAR (W/m2)"         = "APAR",
                   "VPD (Pa)"            = "VPD",
                   "GPP (umol/m2/s-1)"   = "GPP")

ctrls <- ggplot()
for (c in unique(fig_4_df$variable)) {
  df <- fig_4_df %>% filter(variable == c)
  ctrls <- ctrls + new_scale_color() + geom_point(data = df, aes(x = Longitude, y = Latitude, color = value), shape = 15, size = 0.25) +
  scale_color_scico(palette = palettes[c], direction = ifelse(palettes[c] %in% c("roma", "oslo"), -1, 1), name = paste(legend_labels[c]))
}
ctrl_plot <- ctrls +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(Year ~ variable) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  standardized_theme +
  theme(legend.position = "bottom", legend.key.width = unit(0.62, "cm"), axis.title.x = element_blank(), axis.title.y = element_blank())


ggsave("~/Desktop/new_ctrl_figure.pdf", ctrl_plot, width = 10, height = 4.5, units = "in")


```


## BIG BEAUTIFUL PLOT (+ Delta GPP Plot) (5 + 8)

```{r}
range(outside_filtered$delta_VPD_t00X) ## -93, 93
range(outside_filtered$delta_VT_t00X) ## -0.91, 0.91
range(outside_filtered$delta_SMOIS_t00X) ## -0.03, 0.03 ## -0.032, 0.032
range(outside_filtered$delta_APAR_t00X) ## -4.60, 4.60
range(outside_filtered$delta_PSN_t00X) ## -0.91, 0.91 ## -0.98, 0.98

range(inside$delta_VPD_t00X) ## -93, 93
range(inside$delta_GT_t00X) ## -0.91, 0.91
range(inside$delta_SMOIS_t00X) ## -0.03, 0.03 ## -0.032, 0.032
range(inside$delta_SWDOWN_t00X) ## -4.60, 4.60
range(inside$delta_PSN_t00X) ## -0.91, 0.91 ## -0.98, 0.98


mask001 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989),
                      treatment = 1)
mask002 <- data.frame(long = c(-80.13846, -80.15515, -82.00928, -82.27844, -82.26770, -80.41260, -80.13846),
                      lat = c(38.33989, 38.12488, 36.79769, 36.80656, 37.02207, 38.35271, 38.33989),
                      treatment = 2)
mask003 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989),
                      treatment = 3)
mask004 <- data.frame(long = c(-80.13846, -80.18411, -81.46793, -82.2084, -82.17819, -80.89255, -80.13846),
                      lat = c(38.33989, 37.74847, 36.83211, 36.85827, 37.4508, 38.37374, 38.33989),
                      treatment = 4)
mask005 <- data.frame(long = c(-82.19644, -81.51001, -80.22095, -80.26138, -80.93329, -82.22415, -82.19644),
                      lat = c(38.42185, 38.39818, 37.26431, 36.72611, 36.75651, 37.88371, 38.42185),
                      treatment = 5)
mask006 <- data.frame(long = c(-82.19644, -81.92181, -80.24530, -80.26138, -80.53009, -82.26758, -82.19644),
                      lat = c(38.42185, 38.41282, 36.94141, 36.72611, 36.73870, 38.20664, 38.42185),
                      treatment = 6)
masks <- bind_rows(mask001, mask002, mask003, mask004, mask005, mask006)

X.VPD <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_VPD_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_VPD_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("Pa"), limits = range(c(-93, 93))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("c) " * Delta * "VPD")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.VT <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_VT_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_GT_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("K"), limits = range(c(-0.91, 0.91))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("b) " * Delta * "GT (inside) and " * Delta * "VT (outside)")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.SM <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_SMOIS_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_SMOIS_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("m3/m3"), limits = range(c(-0.038, 0.038)), breaks = (c(-0.015, 0.015))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("d) " * Delta * "SM")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.APAR <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_APAR_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_SWDOWN_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("W/m2"), limits = range(c(-4.60, 4.60))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("a) " * Delta * "SW (inside) and " * Delta * "APAR (outside)")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

full_6789 <- ggarrange(X.APAR, X.VT, X.VPD, X.SM, ncol = 1)

ggsave("~/Desktop/full_corrected.pdf", full_6789, width = 14.5, height = 19, units = "in")

average_precip_deciduous_CTRL_17 <- mean(ctrl_17$Mean_CTRL_RAINNC) * 234
average_precip_deciduous_CTRL_18 <- mean(ctrl_18$Mean_CTRL_RAINNC) * 234

average_precip_deciduous_CTRL_18-average_precip_deciduous_CTRL_17

percent_difference <- (average_precip_deciduous_CTRL_18-average_precip_deciduous_CTRL_17) / ((average_precip_deciduous_CTRL_18+average_precip_deciduous_CTRL_17)/2)*100

X.GPP <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_PSN_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("GPP (umol co2/m2/s)"), limits = range(c(-0.98, 0.98))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "bottom")

ggsave("~/Desktop/X.GPP_corrected.pdf", X.GPP, width = 12, height = 4.5, units = "in")
```


## Environmental Context Dot Plot (Inside and Outside) (Figure 6)

```{r}
## OUTSIDE
gpp.mod.carter <- glm(delta_PSN_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_GPP:as.factor(treatment):as.factor(year), outside_filtered, family="gaussian")
sm.mod.carter <- glm(delta_SMOIS_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_SM:as.factor(treatment):as.factor(year), outside_filtered, family="gaussian")
vpd.mod.carter <- glm(delta_VPD_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_VPD:as.factor(treatment):as.factor(year), outside_filtered, family="gaussian")
vt.mod.carter <- glm(delta_VT_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_VT:as.factor(treatment):as.factor(year), outside_filtered, family="gaussian")
apar.mod.carter <- glm(delta_APAR_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_APAR:as.factor(treatment):as.factor(year), outside_filtered, family="gaussian")

outside_filtered2 <- outside_filtered %>% filter(year == 2017, treatment == 1)
lm(outside_filtered2$delta_VPD_t00X ~ outside_filtered2$normalized_ctrl_VPD)

make_awful_carter_table <- function(fit, var){
  cf  <- summary(fit)$coefficients
  idx <- grep("normalized_ctrl", rownames(cf))
  trm <- rownames(cf)[idx]
  data.frame(variable = var,
             year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
             p_val = cf[idx, 4],
             slope = cf[idx, 1],
             row.names = NULL)
}

gpp.mod.carter.mods <- make_awful_carter_table(gpp.mod.carter, "GPP")
sm.mod.carter.mods <- make_awful_carter_table(sm.mod.carter, "SM")
vpd.mod.carter.mods <- make_awful_carter_table(vpd.mod.carter, "VPD")
vt.mod.carter.mods <- make_awful_carter_table(vt.mod.carter, "VT")
apar.mod.carter.mods <- make_awful_carter_table(apar.mod.carter, "APAR")

all_mods_table_carter <- bind_rows(gpp.mod.carter.mods, sm.mod.carter.mods, vpd.mod.carter.mods, vt.mod.carter.mods, apar.mod.carter.mods) %>% 
  mutate(p_val = ifelse(p_val > 0.01, NA, p_val))

range(gpp.mod.carter.mods$slope) #-0.219, 0.219
range(sm.mod.carter.mods$slope) #-0.00372, 0.00372 #-0.00373, 0.00373
range(vpd.mod.carter.mods$slope) #-33.57, 33.57 #-33.73, 33.73
range(vt.mod.carter.mods$slope) #-5.17, 5.17 #-6.24, 6.24
range(apar.mod.carter.mods$slope) #-3.51, 3.51 #-3.68, 3.68

mods_graph_legend_labels_carter <- c("APAR" = "APAR", "GPP" = "GPP", "SM" = "SM", "VPD" = "VPD", "VT" = "VT")

scico_lims_carter <- list("APAR" = c(-3.68, 3.68),
                   "GPP" = c(-0.219, 0.219),
                   "SM" = c(-0.00373, 0.00373),
                   "VPD" = c(-33.73, 33.73),
                   "VT" = c(-6.24, 6.24))

scico_breaks_carter <- list("APAR" = c(-2, 0, 2),
                   "GPP" = c(-0.1, 0, 0.1),
                   "SM" = c(-0.002, 0.002),
                   "VPD" = c(-15, 0, 15),
                   "VT" = c(-2.5, 0, 2.5))

mods_graph_carter <- ggplot()
for (g in unique(all_mods_table_carter$variable)) {
  df <- all_mods_table_carter %>% filter(variable == g)
  mods_graph_carter <- mods_graph_carter + new_scale_color() + geom_point(data = df, aes(x = treatment, y = as.factor(year), color = slope, size = pmin(-log10(p_val), 10))) +
  scale_color_scico(palette = "vik", name = paste(mods_graph_legend_labels_carter[g]), direction = -1, limits = scico_lims_carter[[g]], breaks = scico_breaks_carter[[g]])
}
save_mods_graph_carter <- mods_graph_carter + 
  facet_wrap( ~ variable, nrow = 1) +
  theme_bw() +
  coord_fixed(ratio = 1) +
  labs(x = "Deforestation Scenario", y = "Year", size = NULL, title = "b) Outside Environmental Variables") +
  theme(legend.position = "bottom", legend.key.width = unit(0.62, "cm"), strip.text = element_text(size = 14), plot.title = element_text(size = 16))



## INSIDE
def2_glm_SW <- glm(delta_SWDOWN_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_SW:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_GT <- glm(delta_GT_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_GT:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_VPD <- glm(delta_VPD_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_VPD:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_SM <- glm(delta_SMOIS_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_SM:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_ET <- glm(delta_ET_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_ET:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_PRCP <- glm(delta_RAINNC_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_PRCP:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def2_glm_W <- glm(delta_W_t00X ~ 0 + as.factor(treatment):as.factor(year) + normalized_ctrl_W:as.factor(treatment):as.factor(year), inside, family = "gaussian")

make_awful_carter_table_def2 <- function(fit, var){
  cf  <- summary(fit)$coefficients
  idx <- grep("normalized_ctrl", rownames(cf))
  trm <- rownames(cf)[idx]
  data.frame(variable = var,
             year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
             p_val = cf[idx, 4],
             slope = cf[idx, 1],
             row.names = NULL)
}

def2_GT.mods <- make_awful_carter_table_def2(def2_glm_GT, "GT")
def2_VPD.mods <- make_awful_carter_table_def2(def2_glm_VPD, "VPD")
def2_SW.mods <- make_awful_carter_table_def2(def2_glm_SW, "SW")
def2_SM.mods <- make_awful_carter_table_def2(def2_glm_SM, "SM")
def2_ET.mods <- make_awful_carter_table_def2(def2_glm_ET, "ET")
def2_PRCP.mods <- make_awful_carter_table_def2(def2_glm_PRCP, "PRCP")
def2_W.mods <- make_awful_carter_table_def2(def2_glm_W, "W")

all_mods_table_def2 <- bind_rows(def2_GT.mods, def2_VPD.mods, def2_SW.mods, def2_SM.mods, def2_ET.mods, def2_PRCP.mods, def2_W.mods) %>% 
  mutate(p_val = ifelse(p_val > 0.01, NA, p_val))

range(def2_GT.mods$slope) #-138.63, 138.63 #-139.71, 139.71
range(def2_VPD.mods$slope) #-281, 281 #-284.07, 284.07
range(def2_SW.mods$slope) #-67.03, 67.03 #-66.84, 66.84
range(def2_SM.mods$slope) #-0.105, 0.105 
range(def2_ET.mods$slope) #-6.95e-05, 6.95e-05 #-7.45e-05, 7.45e-05
range(def2_PRCP.mods$slope) #-0.969, 0.969
range(def2_W.mods$slope) #-0.0110, 0.0110


mods_graph_legend_labels_def2 <- c("GT" = "GT", "VPD" = "VPD", "SW" = "SW", "SM" = "SM", "ET" = "ET", "PRCP" = "PRCP", "W" = "W")

#var_temp <- all_mods_table$variable == "SM"
#range(all_mods_table$slope[var_temp])

scico_lims2 <- list("GT" = c(-139.71, 139.71),
                   "VPD" = c(-284.07, 284.07),
                   "SW" = c(-66.84, 66.84),
                   "SM" = c(-0.105, 0.105),
                   "ET" = c(-7.45e-05, 7.45e-05),
                   "PRCP" = c(-0.969, 0.969),
                   "W" = c(-0.0110, 0.0110))

scico_breaks2 <- list("GT" = c(-65, 65),
                   "VPD" = c(-150, 150),
                   "SW" = c(-50, 50),
                   "SM" = c(-0.06, 0.06),
                   "ET" = c(-5e-05, 5e-05),
                   "PRCP" = c(-0.50, 0.50),
                   "W" = c(-0.006, 0.006))


mods_graph_carter2 <- ggplot()
for (g in unique(all_mods_table_def2$variable)) {
  df <- all_mods_table_def2 %>% filter(variable == g)
  mods_graph_carter2 <- mods_graph_carter2 + new_scale_color() + geom_point(data = df, aes(x = treatment, y = as.factor(year), color = slope, size = pmin(-log10(p_val), 10))) +
  scale_color_scico(palette = "bam", name = paste(mods_graph_legend_labels_def2[g]), direction = -1, limits = scico_lims2[[g]], breaks = scico_breaks2[[g]])
}
save_mods_graph_carter_def2 <- mods_graph_carter2 + 
  facet_wrap( ~ variable, nrow = 1) +
  theme_bw() +
  coord_fixed(ratio = 1) +
  labs(x = "Deforestation Scenario", y = "Year", size = NULL, title = "a) Inside Environmental Variables") +
  theme(legend.position = "bottom", legend.key.width = unit(0.62, "cm"), strip.text = element_text(size = 14), plot.title = element_text(size = 16))
#size = "min(-log10(p),10)"

combined_S1_6 <- ggarrange(save_mods_graph_carter_def2, save_mods_graph_carter, ncol = 1)

ggsave("~/Desktop/combined_S1_6_NEW.pdf", combined_S1_6, width = 17, height = 6, units = "in")

```


## Spatial Attenuation Dot Plot (Figure 7)

```{r}
glm_SM <- glm(delta_SMOIS_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + distance_to_LU16_km:theta_bucket:as.factor(treatment):as.factor(year), outside_filtered, family = "gaussian")
glm_VT <- glm(delta_VT_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + distance_to_LU16_km:theta_bucket:as.factor(treatment):as.factor(year), outside_filtered, family = "gaussian")
glm_VPD <- glm(delta_VPD_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + distance_to_LU16_km:theta_bucket:as.factor(treatment):as.factor(year), outside_filtered, family = "gaussian")
glm_APAR <- glm(delta_APAR_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + distance_to_LU16_km:theta_bucket:as.factor(treatment):as.factor(year), outside_filtered, family = "gaussian")
glm_GPP <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + distance_to_LU16_km:theta_bucket:as.factor(treatment):as.factor(year), outside_filtered, family = "gaussian")


#test_VPD <- outside_filtered %>% select(delta_VPD_t00X, distance_to_LU16_km, theta_bucket, treatment, year) %>% filter(year == 2017, treatment == 1, theta_bucket == "bucket2")

#ggplot(data = test_VPD) +
#  geom_point(aes(x = distance_to_LU16_km, y = delta_VPD_t00X)) +
#  geom_smooth(aes(x = distance_to_LU16_km, y = delta_VPD_t00X), method = "lm") +
#  theme_bw()

#lm(test_VPD$delta_VPD_t00X ~ test_VPD$distance_to_LU16_km)


make_awful_table <- function(fit, var){
  cf  <- summary(fit)$coefficients
  idx <- grep("distance_to_LU16_km", rownames(cf))
  trm <- rownames(cf)[idx]
  data.frame(theta_bucket = sub(".*theta_bucketbucket([^:]+):.*", "\\1", trm),
             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
             year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
             variable = var,
             p_val = cf[idx, 4],
             slope = cf[idx, 1],
             row.names = NULL)
}

VT.mods <- make_awful_table(glm_VT, "VT")
VPD.mods <- make_awful_table(glm_VPD, "VPD")
SM.mods <- make_awful_table(glm_SM, "SM")
APAR.mods <- make_awful_table(glm_APAR, "APAR")
GPP.mods <- make_awful_table(glm_GPP, "GPP")

all_mods_table <- bind_rows(VT.mods, VPD.mods, SM.mods, APAR.mods, GPP.mods) %>% 
  mutate(p_val = ifelse(p_val > 0.01, NA, p_val))

all_mods_table <- all_mods_table %>% mutate(theta_bucket2 = recode(theta_bucket, '1' = "ENE", '2' = "NNE", '3' = "NNW", '4' = "WNW", '5' = "WSW", '6' = "SSW", '7' = "SSE", '8' = "ESE"))
all_mods_table$theta_bucket2 <- factor(all_mods_table$theta_bucket2, levels = c("ENE", "NNE", "NNW", "WNW", "WSW", "SSW", "SSE", "ESE"))

range(VT.mods$slope) #-0.00463, 0.00463
range(VPD.mods$slope) #-0.828, 0.828 #-0.804, 0.804
range(SM.mods$slope) #-0.000202, 0.000202
range(APAR.mods$slope) #-0.0174, 0.0174
range(GPP.mods$slope) #-0.00477, 0.00477


mods_graph_legend_labels <- c("APAR" = "APAR", "GPP" = "GPP", "SM" = "SM", "VPD" = "VPD", "VT" = "VT")

scico_lims <- list("APAR" = c(-0.0174, 0.0174),
                   "GPP" = c(-0.00477, 0.00477),
                   "SM" = c(-0.000202, 0.000202),
                   "VPD" = c(-0.804, 0.804),
                   "VT" = c(-0.00463, 0.00463))

scico_breaks <- list("APAR" = c(-0.01, 0.01),
                   "GPP" = c(-0.0025, 0.0025),
                   "SM" = c(-0.0001, 0.0001),
                   "VPD" = c(-0.40, 0.40),
                   "VT" = c(-0.0023, 0.0023))

#attenuation_intercepts <- function(fit, var){
#  cf  <- summary(fit)$coefficients
#  idx <- grep("theta_bucketbucket.*as\\.factor\\(treatment\\).*as\\.factor\\(year\\)[^:]*$", rownames(cf))
#  trm <- rownames(cf)[idx]
#  data.frame(theta_bucket = sub(".*theta_bucketbucket([^:]+):.*", "\\1", trm),
#             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
#             year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
#             variable = var,
#             p_val = cf[idx, 4],
#             slope = cf[idx, 1],
#             row.names = NULL)
#}

#VT.intercepts <- attenuation_intercepts(glm_VT, "VT")
#VPD.intercepts <- attenuation_intercepts(glm_VPD, "VPD")
#SM.intercepts <- attenuation_intercepts(glm_SM, "SM")
#APAR.intercepts <- attenuation_intercepts(glm_APAR, "APAR")
#GPP.intercepts <- attenuation_intercepts(glm_GPP, "GPP")

#all_intercepts_table <- bind_rows(VT.intercepts, VPD.intercepts, SM.intercepts, APAR.intercepts, GPP.intercepts) %>% 
#  mutate(intercept = slope,
#         intercept = ifelse(p_val > 0.01, NA, intercept),
#         pos_neg_intercept = ifelse(intercept > 0, "+", "-")) %>% select(-slope, -p_val)

#all_mods_table <- left_join(all_mods_table, all_intercepts_table, by = c("theta_bucket", "treatment", "year", "variable"))


mods_graph <- ggplot()
for (g in unique(all_mods_table$variable)) {
  df <- all_mods_table %>% filter(variable == g)
  mods_graph <- mods_graph + new_scale_color() + geom_point(data = df, aes(x = treatment, y = theta_bucket2, size = pmin(-log10(p_val), 10), color = slope)) +
  scale_color_scico(palette = "vik", name = paste(mods_graph_legend_labels[g]), direction = -1, limits = scico_lims[[g]], breaks = scico_breaks[[g]])
}
save_mods_graph <- mods_graph + 
  facet_grid(year ~ variable) +
  theme_bw() +
  coord_fixed(ratio = 0.75) +
  labs(x = "Deforestation Scenario", size = NULL, y = "Cardinal Direction", color = NULL) +
  theme(legend.position = "bottom", legend.key.width = unit(0.62, "cm"), strip.text = element_text(size = 16))


#, axis.title.x = element_blank(), axis.title.y = element_blank()

ggsave("~/Desktop/FIG11_NEW2.pdf", save_mods_graph, width = 14, height = 6.5, units = "in")

```


## BIG BEAUTIFUL SECOND PLOT (SUPPLEMENTAL FIGURE S2)

```{r}
range(outside_filtered$delta_ALBEDO_t00X)
range(outside_filtered$delta_RAINNC_t00X)
range(outside_filtered$delta_ET_t00X)
range(outside_filtered$delta_W_t00X)

range(inside$delta_ALBEDO_t00X) ## -0.053, 0.053
range(inside$delta_RAINNC_t00X) ## -2.35, 2.35
range(inside$delta_ET_t00X) ## -1.74e-05, 1.74e-05
range(inside$delta_W_t00X) ## -0.172, 0.172


mask001 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989),
                      treatment = 1)
mask002 <- data.frame(long = c(-80.13846, -80.15515, -82.00928, -82.27844, -82.26770, -80.41260, -80.13846),
                      lat = c(38.33989, 38.12488, 36.79769, 36.80656, 37.02207, 38.35271, 38.33989),
                      treatment = 2)
mask003 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989),
                      treatment = 3)
mask004 <- data.frame(long = c(-80.13846, -80.18411, -81.46793, -82.2084, -82.17819, -80.89255, -80.13846),
                      lat = c(38.33989, 37.74847, 36.83211, 36.85827, 37.4508, 38.37374, 38.33989),
                      treatment = 4)
mask005 <- data.frame(long = c(-82.19644, -81.51001, -80.22095, -80.26138, -80.93329, -82.22415, -82.19644),
                      lat = c(38.42185, 38.39818, 37.26431, 36.72611, 36.75651, 37.88371, 38.42185),
                      treatment = 5)
mask006 <- data.frame(long = c(-82.19644, -81.92181, -80.24530, -80.26138, -80.53009, -82.26758, -82.19644),
                      lat = c(38.42185, 38.41282, 36.94141, 36.72611, 36.73870, 38.20664, 38.42185),
                      treatment = 6)
masks <- bind_rows(mask001, mask002, mask003, mask004, mask005, mask006)

X.ALBEDO <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_ALBEDO_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_ALBEDO_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("--"), limits = range(c(-0.053, 0.053))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("a) " * Delta * "ALBEDO")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.ET <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_ET_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_ET_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("mm s" ^{-1}), limits = range(c(-1.74e-05, 1.74e-05))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("b) " * Delta * "ET")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.PRCP <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_RAINNC_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_RAINNC_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("mm day" ^{-1}), limits = range(c(-2.35, 2.35)), breaks = (c(-1, 1))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("c) " * Delta * "PRCP")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

X.W <- ggplot() +
  geom_point(data = outside_filtered, aes(x = Longitude, y = Latitude, color = delta_W_t00X), shape = 15, size = 0.33) +
  geom_point(data = inside, aes(x = Longitude, y = Latitude, color = delta_W_t00X), shape = 15, size = 0.33) +
  scale_color_scico(palette = "vik", direction = -1, name = expression("m s" ^{-1}), limits = range(c(-0.172, 0.172))) +
  geom_sf(data = combined_regions, color = "grey", linewidth = 0.1, alpha = 0) + 
  geom_polygon(data = masks, aes(x = long, y = lat), color = "green", fill = NA, linewidth = 0.5) +
  #geom_sf(data = selected_states, fill = "NA", color = "black", linewidth = 0.2) +
  scale_x_continuous(breaks = c(-80, -82.5)) +
  scale_y_continuous(breaks = c(37, 38.5)) +
  theme_test() +
  facet_grid(year ~ treatment) +
  labs(x = NULL, y = NULL, title = expression("d) " * Delta * "W (vertical windspeed)")) +
  coord_sf(xlim = c(-83.4, -79), ylim = c(36, 39.1), expand = FALSE) +
  #standardized_theme +
  theme(axis.title = element_text(size = 12, face = "bold"), plot.title = element_text(size = 16), legend.position = "right")

full_6789_supplement <- ggarrange(X.ALBEDO, X.ET, X.PRCP, X.W, ncol = 1)

ggsave("~/Desktop/full_supplement.pdf", full_6789_supplement, width = 14.5, height = 19, units = "in")
```



===========================================================



######## TABLES ########

## Inside Environmental Characteristics Table (Table 3)

```{r}
inside_data <- inside %>% group_by(year, treatment) %>% summarize(before_ALBEDO = mean(Mean_CTRL_ALBEDO),
                                                                  delta_ALBEDO = mean(delta_ALBEDO_t00X),
                                                                  percent_ALBEDO = (mean(delta_ALBEDO_t00X)/mean(Mean_CTRL_ALBEDO))*100,
                                                                  
                                                                  before_GT = mean(Mean_CTRL_GT),
                                                                  delta_GT = mean(delta_GT_t00X),
                                                                  percent_GT = (mean(delta_GT_t00X)/mean(Mean_CTRL_GT))*100,
                                                                  
                                                                  before_ET = mean(Mean_CTRL_ET),
                                                                  delta_ET = mean(delta_ET_t00X),
                                                                  percent_ET = (mean(delta_ET_t00X)/mean(Mean_CTRL_ET))*100,
                                                                  
                                                                  before_SWDOWN = mean(Mean_CTRL_SWDOWN),
                                                                  delta_SWDOWN = mean(delta_SWDOWN_t00X),
                                                                  percent_SWDOWN = (mean(delta_SWDOWN_t00X)/mean(Mean_CTRL_SWDOWN))*100,
                                                                  
                                                                  before_RAINNC = mean(Mean_CTRL_RAINNC),
                                                                  delta_RAINNC = mean(delta_RAINNC_t00X),
                                                                  percent_RAINNC = (mean(delta_RAINNC_t00X)/mean(Mean_CTRL_RAINNC))*100,
                                                                  
                                                                  before_SM = mean(Mean_CTRL_SMOIS),
                                                                  delta_SM = mean(delta_SMOIS_t00X),
                                                                  percent_SM = (mean(delta_SMOIS_t00X)/mean(Mean_CTRL_SMOIS))*100,
                                                                  
                                                                  before_VPD = mean(Mean_CTRL_VPD),
                                                                  delta_VPD = mean(delta_VPD_t00X),
                                                                  percent_VPD = (mean(delta_VPD_t00X)/mean(Mean_CTRL_VPD))*100,
                                                                  
                                                                  before_W = mean(Mean_CTRL_W),
                                                                  delta_W = mean(delta_W_t00X),
                                                                  other_delta_W = (mean(delta_W_t00X)/mean(Mean_CTRL_W))*100,
                                                                  
                                                                  before_WS = sqrt(mean(Mean_CTRL_U)^2 + mean(Mean_CTRL_V)^2),
                                                                  after_WS = sqrt(mean(Mean_t00X_U)^2 + mean(Mean_t00X_V)^2),
                                                                  delta_WS = after_WS - before_WS,
                                                                  percent_WS = ((after_WS - before_WS)/before_WS)*100,
                                                                  
                                                                  before_WD = atan(mean(Mean_CTRL_V)/mean(Mean_CTRL_U))*(180/pi),
                                                                  after_WD = atan(mean(Mean_t00X_V)/mean(Mean_t00X_U))*(180/pi),
                                                                  delta_WD = after_WD - before_WD) %>% ungroup()
inside_data_transposed <- inside_data %>% mutate(treatment = paste0(year, ", ", treatment)) %>% select(-year) %>% column_to_rownames("treatment") %>% t() %>% as.data.frame()


inside_data_avgs <- inside %>% group_by(year) %>% summarize(treatment = "average",before_ALBEDO = mean(Mean_CTRL_ALBEDO),
                                                                  delta_ALBEDO = mean(delta_ALBEDO_t00X),
                                                                  percent_ALBEDO = (mean(delta_ALBEDO_t00X)/mean(Mean_CTRL_ALBEDO))*100,
                                                                  
                                                                  before_GT = mean(Mean_CTRL_GT),
                                                                  delta_GT = mean(delta_GT_t00X),
                                                                  percent_GT = (mean(delta_GT_t00X)/mean(Mean_CTRL_GT))*100,
                                                                  
                                                                  before_ET = mean(Mean_CTRL_ET),
                                                                  delta_ET = mean(delta_ET_t00X),
                                                                  percent_ET = (mean(delta_ET_t00X)/mean(Mean_CTRL_ET))*100,
                                                                  
                                                                  before_SWDOWN = mean(Mean_CTRL_SWDOWN),
                                                                  delta_SWDOWN = mean(delta_SWDOWN_t00X),
                                                                  percent_SWDOWN = (mean(delta_SWDOWN_t00X)/mean(Mean_CTRL_SWDOWN))*100,
                                                                  
                                                                  before_RAINNC = mean(Mean_CTRL_RAINNC),
                                                                  delta_RAINNC = mean(delta_RAINNC_t00X),
                                                                  percent_RAINNC = (mean(delta_RAINNC_t00X)/mean(Mean_CTRL_RAINNC))*100,
                                                                  
                                                                  before_SM = mean(Mean_CTRL_SMOIS),
                                                                  delta_SM = mean(delta_SMOIS_t00X),
                                                                  percent_SM = (mean(delta_SMOIS_t00X)/mean(Mean_CTRL_SMOIS))*100,
                                                                  
                                                                  before_VPD = mean(Mean_CTRL_VPD),
                                                                  delta_VPD = mean(delta_VPD_t00X),
                                                                  percent_VPD = (mean(delta_VPD_t00X)/mean(Mean_CTRL_VPD))*100,
                                                                  
                                                                  before_W = mean(Mean_CTRL_W),
                                                                  delta_W = mean(delta_W_t00X),
                                                                  other_delta_W = (mean(delta_W_t00X)/mean(Mean_CTRL_W))*100,
                                                                  
                                                                  before_WS = sqrt(mean(Mean_CTRL_U)^2 + mean(Mean_CTRL_V)^2),
                                                                  after_WS = sqrt(mean(Mean_t00X_U)^2 + mean(Mean_t00X_V)^2),
                                                                  delta_WS = after_WS - before_WS,
                                                                  percent_WS = ((after_WS - before_WS)/before_WS)*100,
                                                                  
                                                                  before_WD = atan(mean(Mean_CTRL_V)/mean(Mean_CTRL_U))*(180/pi),
                                                                  after_WD = atan(mean(Mean_t00X_V)/mean(Mean_t00X_U))*(180/pi),
                                                                  delta_WD = after_WD - before_WD) %>% ungroup()

inside_data_avgs_transposed <- inside_data_avgs %>% mutate(treatment = paste0(year, ", ", treatment)) %>% select(-year) %>% column_to_rownames("treatment") %>% t() %>% as.data.frame()


inside_data_transposed_final <- bind_cols(inside_data_transposed, inside_data_avgs_transposed) %>% select("2017, 1", "2017, 2", "2017, 3", "2017, 4", "2017, 5", "2017, 6", "2017, average", "2018, 1", "2018, 2", "2018, 3", "2018, 4", "2018, 5", "2018, 6", "2018, average")


rounding_function <- function(x) {
  if (is.na(x) || x == 0) return("0.00")
  first_digit_pos <- floor(log10(abs(x)))
  if (first_digit_pos >= 0) {
    target_decimals <- 2
  } else {
    sig_fig_decimals <- abs(first_digit_pos) + 1
    target_decimals <- max(2, sig_fig_decimals)
  }
  formatC(x, format = "f", digits = target_decimals)
}
rounding_function_vec <- Vectorize(rounding_function)
inside_data_transposed_final_formatted <- inside_data_transposed_final %>%
  mutate(across(where(is.numeric), rounding_function_vec))


kable(inside_data_transposed_final_formatted, format = "latex", booktabs = TRUE)

```


## Spatial vs. Topographic Regressions (inside) Table (Table 4)

```{r}
def_glm_GT_topographic <- glm(delta_GT_t00X ~ ELEVATION + SOIL.TYPE, inside, family = "gaussian")
def_glm_VPD_topographic <- glm(delta_VPD_t00X ~ ELEVATION + SOIL.TYPE, inside, family = "gaussian")
def_glm_SM_topographic <- glm(delta_SMOIS_t00X ~ ELEVATION + SOIL.TYPE, inside, family = "gaussian")
def_glm_ET_topographic <- glm(delta_ET_t00X ~ ELEVATION + SOIL.TYPE, inside, family = "gaussian")

def_glm_GT_spatial <- glm(delta_GT_t00X ~ theta_bucket:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def_glm_VPD_spatial <- glm(delta_VPD_t00X ~ theta_bucket:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def_glm_SM_spatial <- glm(delta_SMOIS_t00X ~ theta_bucket:as.factor(treatment):as.factor(year), inside, family = "gaussian")
def_glm_ET_spatial <- glm(delta_ET_t00X ~ theta_bucket:as.factor(treatment):as.factor(year), inside, family = "gaussian")

def_glm_GT_combined <- glm(delta_GT_t00X ~ theta_bucket:as.factor(treatment):as.factor(year) + SOIL.TYPE + ELEVATION, inside, family = "gaussian")
def_glm_VPD_combined <- glm(delta_VPD_t00X ~ theta_bucket:as.factor(treatment):as.factor(year) + SOIL.TYPE + ELEVATION, inside, family = "gaussian")
def_glm_SM_combined <- glm(delta_SMOIS_t00X ~ theta_bucket:as.factor(treatment):as.factor(year) + SOIL.TYPE + ELEVATION, inside, family = "gaussian")
def_glm_ET_combined <- glm(delta_ET_t00X ~ theta_bucket:as.factor(treatment):as.factor(year) + SOIL.TYPE + ELEVATION, inside, family = "gaussian")


inside_regressions <- data.frame(Variable = c("GT", "VPD", "SM", "ET"),
                                 Statistic = "AIC",
                                 Combined = c(AIC(def_glm_GT_combined), AIC(def_glm_VPD_combined), AIC(def_glm_SM_combined), AIC(def_glm_ET_combined)),
                                 Topographic = c(AIC(def_glm_GT_topographic), AIC(def_glm_VPD_topographic), AIC(def_glm_SM_topographic), AIC(def_glm_ET_topographic)),
                                 Spatial = c(AIC(def_glm_GT_spatial), AIC(def_glm_VPD_spatial), AIC(def_glm_SM_spatial), AIC(def_glm_ET_spatial)))

inside_regressions_deltas <- data.frame(Variable = c("GT", "VPD", "SM", "ET"),
                                 Statistic = "deltaAIC",
                                 Combined = c(AIC(def_glm_GT_combined) - AIC(def_glm_GT_combined), AIC(def_glm_VPD_combined) - AIC(def_glm_VPD_combined), AIC(def_glm_SM_combined) - AIC(def_glm_SM_combined), AIC(def_glm_ET_combined) - AIC(def_glm_ET_combined)),
                                 Topographic = c(AIC(def_glm_GT_topographic) - AIC(def_glm_GT_combined), AIC(def_glm_VPD_topographic) - AIC(def_glm_VPD_combined), AIC(def_glm_SM_topographic) - AIC(def_glm_SM_combined), AIC(def_glm_ET_topographic) - AIC(def_glm_ET_combined)),
                                 Spatial = c(AIC(def_glm_GT_spatial) - AIC(def_glm_GT_combined), AIC(def_glm_VPD_spatial) - AIC(def_glm_VPD_combined), AIC(def_glm_SM_spatial) - AIC(def_glm_SM_combined), AIC(def_glm_ET_spatial) - AIC(def_glm_ET_combined)))

inside_model_table <- bind_rows(inside_regressions, inside_regressions_deltas) %>% group_by(Variable)

kable(inside_model_table, format = "latex", digits = 2, booktabs = TRUE)
```


## Outside Environmental Characteristics Table (Table 5)

```{r}
outside_data <- outside_filtered %>% group_by(year, treatment) %>% summarize(before_APAR = mean(Mean_CTRL_APAR),
                                                                             delta_APAR = mean(delta_APAR_t00X),
                                                                             percent_APAR = (mean(delta_APAR_t00X)/mean(Mean_CTRL_APAR))*100,
                                                                             
                                                                             before_VT = mean(Mean_CTRL_VT),
                                                                             delta_VT = mean(delta_VT_t00X),
                                                                             percent_VT = (mean(delta_VT_t00X)/mean(Mean_CTRL_VT))*100,
                                                                             
                                                                             before_SM = mean(Mean_CTRL_SMOIS),
                                                                             delta_SM = mean(delta_SMOIS_t00X),
                                                                             percent_SM = (mean(delta_SMOIS_t00X)/mean(Mean_CTRL_SMOIS))*100,
                                                                             
                                                                             before_VPD = mean(Mean_CTRL_VPD),
                                                                             delta_VPD = mean(delta_VPD_t00X),
                                                                             percent_VPD = (mean(delta_VPD_t00X)/mean(Mean_CTRL_VPD))*100,
                                                                             
                                                                             before_GPP = mean(Mean_CTRL_PSN),
                                                                             delta_GPP = mean(delta_PSN_t00X),
                                                                             percent_GPP = (mean(delta_PSN_t00X)/mean(Mean_CTRL_PSN))*100) %>% ungroup()
outside_data_transposed <- outside_data %>% mutate(treatment = paste0(year, ", ", treatment)) %>% select(-year) %>% column_to_rownames("treatment") %>% t() %>% as.data.frame()


outside_data_avgs <- outside_filtered %>% group_by(year) %>% summarize(treatment = "average",
                                                                       
                                                                       before_APAR = mean(Mean_CTRL_APAR),
                                                                       delta_APAR = mean(delta_APAR_t00X),
                                                                       percent_APAR = (mean(delta_APAR_t00X)/mean(Mean_CTRL_APAR))*100,
                                                                       
                                                                       before_VT = mean(Mean_CTRL_VT),
                                                                       delta_VT = mean(delta_VT_t00X),
                                                                       percent_VT = (mean(delta_VT_t00X)/mean(Mean_CTRL_VT))*100,
                                                                       
                                                                       before_SM = mean(Mean_CTRL_SMOIS),
                                                                       delta_SM = mean(delta_SMOIS_t00X),
                                                                       percent_SM = (mean(delta_SMOIS_t00X)/mean(Mean_CTRL_SMOIS))*100,
                                                                       
                                                                       before_VPD = mean(Mean_CTRL_VPD),
                                                                       delta_VPD = mean(delta_VPD_t00X),
                                                                       percent_VPD = (mean(delta_VPD_t00X)/mean(Mean_CTRL_VPD))*100,
                                                                       
                                                                       before_GPP = mean(Mean_CTRL_PSN),
                                                                       delta_GPP = mean(delta_PSN_t00X),
                                                                       percent_GPP = (mean(delta_PSN_t00X)/mean(Mean_CTRL_PSN))*100) %>% ungroup()
outside_data_avgs_transposed <- outside_data_avgs %>% mutate(treatment = paste0(year, ", ", treatment)) %>% select(-year) %>% column_to_rownames("treatment") %>% t() %>% as.data.frame()


outside_data_transposed_final <- bind_cols(outside_data_transposed, outside_data_avgs_transposed) %>% select("2017, 1", "2017, 2", "2017, 3", "2017, 4", "2017, 5", "2017, 6", "2017, average", "2018, 1", "2018, 2", "2018, 3", "2018, 4", "2018, 5", "2018, 6", "2018, average")


rounding_function <- function(x) {
  if (is.na(x) || x == 0) return("0.00")
  first_digit_pos <- floor(log10(abs(x)))
  if (first_digit_pos >= 0) {
    target_decimals <- 2
  } else {
    sig_fig_decimals <- abs(first_digit_pos) + 1
    target_decimals <- max(2, sig_fig_decimals)
  }
  formatC(x, format = "f", digits = target_decimals)
}
rounding_function_vec <- Vectorize(rounding_function)
outside_data_transposed_final_formatted <- outside_data_transposed_final %>%
  mutate(across(where(is.numeric), rounding_function_vec))


kable(outside_data_transposed_final_formatted, format = "latex", booktabs = TRUE)
```


## GPP GLM Table (Table 6/7)

```{r}
intercept.glm <- glm(delta_PSN_t00X ~ 1, data = outside_filtered, family = gaussian)
null.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year), data = outside_filtered, family = gaussian)
AVG.CTRL.GPP.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + Mean_CTRL_PSN, data = outside_filtered, family = gaussian)
X.APAR.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_APAR_t00X, data = outside_filtered, family = gaussian)
X.SM.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_SMOIS_t00X, data = outside_filtered, family = gaussian)
X.VT.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_VT_t00X, data = outside_filtered, family = gaussian)
X.VPD.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_VPD_t00X, data = outside_filtered, family = gaussian)
APAR.VT.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_VT_t00X + delta_APAR_t00X, data = outside_filtered, family = gaussian)
APAR.VT.SM.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_APAR_t00X + delta_VT_t00X + delta_SMOIS_t00X, data = outside_filtered, family = gaussian)
APAR.VT.SM.VPD.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_APAR_t00X + delta_VT_t00X + delta_SMOIS_t00X + delta_VPD_t00X, data = outside_filtered, family = gaussian)
APAR.VT.SM.VPD.AVG_CTRL.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + delta_APAR_t00X + delta_VT_t00X + delta_SMOIS_t00X + delta_VPD_t00X + Mean_CTRL_PSN, data = outside_filtered, family = gaussian)


best.model.glm <- glm(delta_PSN_t00X ~ 0 + theta_bucket:as.factor(treatment):as.factor(year) + as.factor(treatment):theta_bucket:distance_to_LU16_km:as.factor(year) + as.factor(year):as.factor(treatment):delta_APAR_t00X + as.factor(year):as.factor(treatment):delta_VT_t00X + as.factor(year):as.factor(treatment):delta_SMOIS_t00X + as.factor(year):as.factor(treatment):delta_VPD_t00X + as.factor(year):as.factor(treatment):Mean_CTRL_PSN, data = outside_filtered, family = gaussian)

#GLM_Table <- data.frame(VARIABLE = c("Intercept Only", "Base Model", "AVG.CTRL.GPP", "X.APAR", "X.SM", "X.VT", "X.VPD", "X.VT + X.APAR", "X.VT + X.APAR + X.SM", "X.VT + X.APAR + X.SM + X.VPD"),
#                        AIC = c(AIC(intercept.glm), AIC(null.glm), AIC(AVG.CTRL.GPP.glm), AIC(X.APAR.glm), AIC(X.SM.glm), AIC(X.VT.glm), AIC(X.VPD.glm), AIC(APAR.VT.glm), AIC(APAR.VT.SM.glm), AIC(APAR.VT.SM.VPD.glm)),
#                        delta_AIC = c(NA, AIC(null.glm)-AIC(intercept.glm), AIC(AVG.CTRL.GPP.glm)-AIC(intercept.glm), AIC(X.APAR.glm)-AIC(intercept.glm), AIC(X.SM.glm)-AIC(intercept.glm), AIC(X.VT.glm)-AIC(intercept.glm), AIC(X.VPD.glm)-AIC(intercept.glm), AIC(APAR.VT.glm)-AIC(intercept.glm), AIC(APAR.VT.SM.glm)-AIC(intercept.glm), AIC(APAR.VT.SM.VPD.glm)-AIC(intercept.glm)))

#kable(GLM_Table, format = "latex", digits = 4, booktabs = TRUE)


Ford_formatted_GLM_Table <- data.frame(VARIABLE = c("Best Model", "X.VT + X.APAR + X.SM + X.VPD + AVG.CTRL.GPP", "X.VT + X.APAR + X.SM + X.VPD", "X.VT + X.APAR + X.SM", "X.SM", "X.VPD", "X.VT + X.APAR", "X.APAR", "X.VT", "AVG.CTRL.GPP", "Base Model", "Intercept Only"),
                                       AIC = c(AIC(best.model.glm), AIC(APAR.VT.SM.VPD.AVG_CTRL.glm), AIC(APAR.VT.SM.VPD.glm), AIC(APAR.VT.SM.glm), AIC(X.SM.glm), AIC(X.VPD.glm), AIC(APAR.VT.glm), AIC(X.APAR.glm), AIC(X.VT.glm), AIC(AVG.CTRL.GPP.glm), AIC(null.glm), AIC(intercept.glm)),
                                       delta_AIC = c(NA, AIC(APAR.VT.SM.VPD.AVG_CTRL.glm)-AIC(best.model.glm), AIC(APAR.VT.SM.VPD.glm)-AIC(best.model.glm), AIC(APAR.VT.SM.glm)-AIC(best.model.glm), AIC(X.SM.glm)-AIC(best.model.glm), AIC(X.VPD.glm)-AIC(best.model.glm), AIC(APAR.VT.glm)-AIC(best.model.glm), AIC(X.APAR.glm)-AIC(best.model.glm), AIC(X.VT.glm)-AIC(best.model.glm), AIC(AVG.CTRL.GPP.glm)-AIC(best.model.glm), AIC(null.glm)-AIC(best.model.glm), AIC(intercept.glm)-AIC(best.model.glm)))

kable(Ford_formatted_GLM_Table, format = "latex", digits = 2, booktabs = TRUE)

summary(best.model.glm)


##THIS CODE SUCKS, BUT WORKS. MODIFIED OTHER CODE IN LAZIEST WAY POSSIBLE. WHOOPS.
last_awful_table <- function(fit){
  cf  <- summary(fit)$coefficients
  idx <- grep("as\\.factor\\(treatment\\).*as\\.factor\\(year\\).*delta_.*", rownames(cf))
  trm <- rownames(cf)[idx]
  data.frame(year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
             variable = sub(".*:(delta_[^:]+)$", "\\1", trm),
             p_val = cf[idx, 4],
             slope = cf[idx, 1],
             row.names = NULL)
}

last_awful_table_for_initialGPP <- function(fit){
  cf  <- summary(fit)$coefficients
  idx <- grep("as\\.factor\\(treatment\\).*as\\.factor\\(year\\).*Mean_.*", rownames(cf))
  trm <- rownames(cf)[idx]
  data.frame(year = sub(".*as\\.factor\\(year\\)([0-9]+).*", "\\1", trm),
             treatment = sub(".*as\\.factor\\(treatment\\)([0-9]+).*", "\\1", trm),
             variable = sub(".*:(Mean_[^:]+)$", "\\1", trm),
             p_val = cf[idx, 4],
             slope = cf[idx, 1],
             row.names = NULL)
}

last.awful.mod.deltas <- last_awful_table(best.model.glm)
last.awful.mod.initialGPP <- last_awful_table_for_initialGPP(best.model.glm)

last.awful.mod <- bind_rows(last.awful.mod.deltas, last.awful.mod.initialGPP)

last.awful.mod.transposed <- last.awful.mod %>% mutate(treatment = paste0(year, ", ", treatment)) %>% select(-year, -p_val) %>% pivot_wider(names_from = "treatment", values_from = "slope")

last.awful.mod.summary <- last.awful.mod %>% group_by(year, variable) %>% summarize(slope = mean(slope)) %>% pivot_wider(names_from = "year", values_from = "slope")
colnames(last.awful.mod.summary) <- c("variable", "AVG2017", "AVG2018")

last.awful.mod.transposed.final <- left_join(last.awful.mod.transposed, last.awful.mod.summary, by = "variable") %>% select("variable", "2017, 1", "2017, 2", "2017, 3", "2017, 4", "2017, 5", "2017, 6", "AVG2017", "2018, 1", "2018, 2", "2018, 3", "2018, 4", "2018, 5", "2018, 6", "AVG2018")



rounding_function <- function(x) {
  if (is.na(x) || x == 0) return("0.00")
  first_digit_pos <- floor(log10(abs(x)))
  if (first_digit_pos >= 0) {
    target_decimals <- 2
  } else {
    sig_fig_decimals <- abs(first_digit_pos) + 1
    target_decimals <- max(2, sig_fig_decimals)
  }
  formatC(x, format = "f", digits = target_decimals)
}
rounding_function_vec <- Vectorize(rounding_function)
last.awful.mod.transposed.final.formatted <- last.awful.mod.transposed.final %>%
  mutate(across(where(is.numeric), rounding_function_vec))


kable(last.awful.mod.transposed.final.formatted, format = "latex", booktabs = TRUE)



#%>% slice(1:60) #%>% separate(year, into = c("year", "treatment", "variable"), sep = ":") #%>% mutate(year = sub("as\\.factor\\(year\\)", "", year), treatment = sub("as\\.factor\\(treatment\\)", "", treatment))

#last.awful.mod.pivoted <- last.awful.mod %>% select(-p_val) %>% pivot_wider(names_from = variable, values_from = slope)
#write.csv(last.awful.mod.pivoted, "~/Desktop/data_for_aov.csv")


#last.awful.mod.2017 <- last.awful.mod %>% filter(year == 2017) %>% select(-p_val, -year) %>% mutate(slope = round(slope, 3)) %>% pivot_wider(names_from = variable, values_from = slope)
#last.awful.mod.2018 <- last.awful.mod %>% filter(year == 2018) %>% select(-p_val, -year) %>% mutate(slope = round(slope, 3)) %>% pivot_wider(names_from = variable, values_from = slope)
#last.awful.mod.summary <- last.awful.mod %>% group_by(year, variable) %>% summarize(slope = mean(slope))
#kable(t(last.awful.mod.2017), format = "latex", digits = 2, booktabs = TRUE)
#kable(t(last.awful.mod.2018), format = "latex", digits = 2, booktabs = TRUE)
#kable(last.awful.mod.summary, format = "latex", digits = 3, booktabs = TRUE)




```


## Best GPP Model TukeyHSD (Table 7)

```{r}

outside_filtered2 <- outside_filtered %>% mutate(year = as.factor(year), treatment = as.factor(treatment))

#best.model.glm2 <- glm(delta_PSN_t00X ~ year:treatment:delta_APAR_t00X + year:treatment:delta_VT_t00X + year:treatment:delta_SMOIS_t00X + year:treatment:delta_VPD_t00X + year:treatment:Mean_CTRL_PSN + theta_bucket:distance_to_LU16_km:year:treatment, data = outside_filtered2, family = gaussian)


best.model.glm2 <- glm(delta_PSN_t00X ~ 0 + theta_bucket:year:treatment + theta_bucket:distance_to_LU16_km:year:treatment + year:treatment:delta_APAR_t00X + year:treatment:delta_VT_t00X + year:treatment:delta_SMOIS_t00X + year:treatment:delta_VPD_t00X + year:treatment:Mean_CTRL_PSN, data = outside_filtered2, family = gaussian)


sm_slopes_compared <- emtrends(best.model.glm2, pairwise ~ year:treatment, nesting = NULL, var = "delta_SMOIS_t00X", adjust = "Tukey")
vt_slopes_compared <- emtrends(best.model.glm2, pairwise ~ year:treatment, nesting = NULL, var = "delta_VT_t00X", adjust = "Tukey")
apar_slopes_compared <- emtrends(best.model.glm2, pairwise ~ year:treatment, nesting = NULL, var = "delta_APAR_t00X", adjust = "Tukey")
vpd_slopes_compared <- emtrends(best.model.glm2, pairwise ~ year:treatment, nesting = NULL, var = "delta_VPD_t00X", adjust = "Tukey")
mean.gpp_slopes_compared <- emtrends(best.model.glm2, pairwise ~ year:treatment, nesting = NULL, var = "Mean_CTRL_PSN", adjust = "Tukey")

sm_slopes_stat_sig <- summary(sm_slopes_compared$contrasts) %>% mutate(significant = ifelse(p.value <= 0.01, 1, 0)) %>% mutate(SM_est_se = paste0(round(estimate,2), "pm", round(SE,2), ifelse(significant == 1, "*", "")))
vt_slopes_stat_sig <- summary(vt_slopes_compared$contrasts) %>% mutate(significant = ifelse(p.value <= 0.01, 1, 0)) %>% mutate(VT_est_se = paste0(round(estimate,3), "pm", round(SE,3), ifelse(significant == 1, "*", "")))
apar_slopes_stat_sig <- summary(apar_slopes_compared$contrasts) %>% mutate(significant = ifelse(p.value <= 0.01, 1, 0)) %>% mutate(APAR_est_se = paste0(round(estimate,4), "pm", round(SE,4), ifelse(significant == 1, "*", "")))
vpd_slopes_stat_sig <- summary(vpd_slopes_compared$contrasts) %>% mutate(significant = ifelse(p.value <= 0.01, 1, 0)) %>% mutate(VPD_est_se = paste0(round(estimate,4), "pm", round(SE,4), ifelse(significant == 1, "*", "")))
mean.gpp_slopes_stat_sig <- summary(mean.gpp_slopes_compared$contrasts) %>% mutate(significant = ifelse(p.value <= 0.01, 1, 0)) %>% mutate(Init.GPP_est_se = paste0(round(estimate,4), "pm", round(SE,4), ifelse(significant == 1, "*", "")))

prop.table(table(sm_slopes_stat_sig$significant))
prop.table(table(vt_slopes_stat_sig$significant))
prop.table(table(apar_slopes_stat_sig$significant))
prop.table(table(vpd_slopes_stat_sig$significant))
prop.table(table(mean.gpp_slopes_stat_sig$significant))

sm_slopes_stat_sig2 <- sm_slopes_stat_sig %>% select(contrast, SM_est_se)
vt_slopes_stat_sig2 <- vt_slopes_stat_sig %>% select(contrast, VT_est_se)
apar_slopes_stat_sig2 <- apar_slopes_stat_sig %>% select(contrast, APAR_est_se)
vpd_slopes_stat_sig2 <- vpd_slopes_stat_sig %>% select(contrast, VPD_est_se)
mean.gpp_slopes_stat_sig2 <- mean.gpp_slopes_stat_sig %>% select(contrast, Init.GPP_est_se)

slopes_table <- left_join(sm_slopes_stat_sig2, vt_slopes_stat_sig2, by = "contrast")
slopes_table <- left_join(slopes_table, apar_slopes_stat_sig2, by = "contrast")
slopes_table <- left_join(slopes_table, vpd_slopes_stat_sig2, by = "contrast")
slopes_table <- left_join(slopes_table, mean.gpp_slopes_stat_sig2, by = "contrast")

#sm_slopes_stat_sig2 <- sm_slopes_stat_sig %>% mutate(SM.p.val = ifelse(p.value <= 0.01, "*", NA)) %>% select(contrast, SM.p.val)
#vt_slopes_stat_sig2 <- vt_slopes_stat_sig %>% mutate(VT.p.val = ifelse(p.value <= 0.01, "*", NA)) %>% select(contrast, VT.p.val)
#apar_slopes_stat_sig2 <- apar_slopes_stat_sig %>% mutate(APAR.p.val = ifelse(p.value <= 0.01, "*", NA)) %>% select(contrast, APAR.p.val)
#vpd_slopes_stat_sig2 <- vpd_slopes_stat_sig %>% mutate(VPD.p.val = ifelse(p.value <= 0.01, "*", NA)) %>% select(contrast, VPD.p.val)
#mean.gpp_slopes_stat_sig2 <- mean.gpp_slopes_stat_sig %>% mutate(Mean.GPP.p.val = ifelse(p.value <= 0.01, "*", NA)) %>% select(contrast, Mean.GPP.p.val)


rounding_function <- function(x) {
  if (is.na(x) || x == 0) return("0.00")
  first_digit_pos <- floor(log10(abs(x)))
  if (first_digit_pos >= 0) {
    target_decimals <- 2
  } else {
    sig_fig_decimals <- abs(first_digit_pos) + 1
    target_decimals <- max(2, sig_fig_decimals)
  }
  formatC(x, format = "f", digits = target_decimals)
}
rounding_function_vec <- Vectorize(rounding_function)
slopes_table.formatted <- slopes_table %>%
  mutate(across(where(is.numeric), rounding_function_vec))


options(knitr.kable.NA = '')
kable(slopes_table.formatted, format = "latex", booktabs = TRUE)
```


## Revisions Data

```{r}
may26_outside_luc1.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.001_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 1)
may26_outside_luc2.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.002_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 2)
may26_outside_luc3.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.003_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 3)
may26_outside_luc4.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.004_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 4)
may26_outside_luc5.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.005_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 5)
may26_outside_luc6.17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.006_deciduous_points_only.csv") %>% mutate(year = 2017, treatment = 6)
may26_outside_luc1.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.001_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 1)
may26_outside_luc2.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.002_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 2)
may26_outside_luc3.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.003_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 3)
may26_outside_luc4.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.004_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 4)
may26_outside_luc5.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.005_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 5)
may26_outside_luc6.18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.006_deciduous_points_only.csv") %>% mutate(year = 2018, treatment = 6)

may26_outside_luc1.17_scaled <- may26_outside_luc1.17 %>% mutate(z_scores = scale(Mean_CTRL_PSN))

ggplot(data = may26_outside_luc1.17_scaled) +
  geom_histogram(aes(x = Mean_t00X_PSN))


may26_outside <- bind_rows(may26_outside_luc1.17, may26_outside_luc2.17, may26_outside_luc3.17, may26_outside_luc4.17, may26_outside_luc5.17, may26_outside_luc6.17,
                                   may26_outside_luc1.18, may26_outside_luc2.18, may26_outside_luc3.18, may26_outside_luc4.18, may26_outside_luc5.18, may26_outside_luc6.18)


mask003 <- data.frame(long = c(-80.13846, -80.17999, -81.60565, -82.27844, -82.25146, -80.82397, -80.13846),
                      lat = c(38.33989, 37.80225, 36.78333, 36.80656, 37.34526, 38.37086, 38.33989))
mask004 <- data.frame(long = c(-80.13846, -80.18411, -81.46793, -82.2084, -82.17819, -80.89255, -80.13846),
                      lat = c(38.33989, 37.74847, 36.83211, 36.85827, 37.4508, 38.37374, 38.33989))
mask003_sf <- st_polygon(list(as.matrix(mask003))) %>% st_sfc(crs = 4326)
mask004_sf <- st_polygon(list(as.matrix(mask004))) %>% st_sfc(crs = 4326)
may26_outside_sf <- st_as_sf(may26_outside, coords = c("Longitude", "Latitude"), crs = 4326)
inside_003 <- st_within(may26_outside_sf, mask003_sf, sparse = FALSE)[,1]
inside_004 <- st_within(may26_outside_sf, mask004_sf, sparse = FALSE)[,1]

keep_point <- case_when(may26_outside_sf$treatment == 3 ~ !inside_003, may26_outside_sf$treatment == 4 ~ !inside_004, TRUE ~ TRUE)
may26_outside_sf <- may26_outside_sf %>% ungroup()
may26_outside_unfiltered <- may26_outside_sf[keep_point, ] %>% mutate(Longitude = st_coordinates(.)[,1], Latitude = st_coordinates(.)[,2]) %>% st_drop_geometry()


may26_outside_unfiltered.for_histogram <- may26_outside_unfiltered %>% mutate(removed_or_kept_gpp = ifelse(Mean_t00X_PSN <= 2, "removed", "kept"),
                                                                              removed_or_kept_deltatemp = ifelse(delta_VT_t00X <= 1 & delta_VT_t00X >= -1, "kept", "removed"),
                                                                              treatment = recode(treatment, '1' = "Scenario 1", '2' = "Scenario 2", '3' = "Scenario 3", '4' = "Scenario 4", '5' = "Scenario 5", '6' = "Scenario 6"))

t00X_filterGPP_plots <- ggplot(data = may26_outside_unfiltered.for_histogram) +
  geom_histogram(aes(x = Mean_t00X_PSN, fill = removed_or_kept_gpp)) +
  facet_grid(year ~ treatment) +
  scale_fill_manual(values = c("kept" = "royalblue2", "removed" = "violetred1")) +
  geom_vline(xintercept = 2, color = "violetred1", linetype = "dashed") +
  theme_test() +
  lims(y = c(0, 1800)) +
  labs(y = NULL, x = expression("Average GPP Following Treatment in Remaining Deciduous Forest Grid Cells (" * mu * "mol CO"[2] * " m"^{-2} * " s" ^{-1} * ")")) +
  theme(legend.position = "none", strip.text = element_text(size = 14))

t00X_filterDeltaVT_plots <- ggplot(data = may26_outside_unfiltered.for_histogram) +
  geom_histogram(aes(x = delta_VT_t00X, fill = removed_or_kept_deltatemp), binwidth = 2) +
  facet_grid(year ~ treatment) +
  scale_fill_manual(values = c("kept" = "royalblue2", "removed" = "violetred1")) +
  geom_vline(xintercept = -1, color = "violetred1", linetype = "dashed") +
  geom_vline(xintercept = 1, color = "violetred1", linetype = "dashed") +
  theme_test() +
  labs(y = "Number of Grid Cells", x = expression(Delta * "Vegetation Temperature in Remaining Deciduous Forest Grid Cells (K)")) +
  theme(legend.position = "none", strip.text = element_text(size = 14))

ctrl_17 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.001_all_points.csv") %>% mutate(treatment = "Controls", year = 2017)
ctrl_18 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.001_all_points.csv") %>% mutate(treatment = "Controls", year = 2018)
ctrl_runs <- bind_rows(ctrl_17, ctrl_18) %>% mutate(removed_or_kept_gpp = ifelse(Mean_CTRL_PSN <= 2, "removed", "kept"), removed_or_kept_deltatemp = NA)


CTRL_filterGPP_plots <- ggplot(data = ctrl_runs) +
  geom_histogram(aes(x = Mean_CTRL_PSN, fill = removed_or_kept_gpp)) +
  facet_grid(year ~ treatment) +
  scale_fill_manual(values = c("kept" = "royalblue2", "removed" = "violetred1")) +
  geom_vline(xintercept = 2, color = "violetred1", linetype = "dashed") +
  theme_test() +
  lims(y = c(0, 1800)) +
  labs(y = "Number of Grid Cells", x = expression("Average Control GPP (" * mu * "mol CO"[2] * " m"^{-2} * " s" ^{-1} * ")")) +
  theme(legend.position = "none", strip.background = element_rect(fill = "springgreen2", color = "darkgreen"), strip.text = element_text(size = 14))




GPP_filter_plots <- ggarrange(CTRL_filterGPP_plots, t00X_filterGPP_plots, widths = c(1,5), labels = c("(A)", "(B)"), hjust = 0.01, font.label = list(size = 16))
#ggsave("~/Desktop/GPP_filter_plots.pdf", GPP_filter_plots, width = 18.25, height = 4.7, units = "in")

all_filter_plots <- ggarrange(GPP_filter_plots, t00X_filterDeltaVT_plots, labels = c("","(C)"), nrow = 2)

ggsave("~/Desktop/all_filter_plots.pdf", all_filter_plots, width = 18.25, height = 10, units = "in")


#theme(legend.position = "bottom", legend.text = element_text(size = 14), legend.title = element_text(size = 14), axis.title = element_text(size = 14), axis.text = element_text(size = 14), strip.text = element_text(size = 16)) + guides(color = guide_legend(nrow = 2), linewidth = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2))



outside_filtered_divided <- split(outside_filtered, list(outside_filtered$year, outside_filtered$treatment))

may26_outside_unfiltered_divided <- split(may26_outside_unfiltered, list(may26_outside_unfiltered$year, may26_outside_unfiltered$treatment))

comparison_of_filtered_unfiltered_outside_2017 <- data.frame(year = 2017, scenario = c(1,2,3,4,5,6),
                                                             before.outside = c(length(may26_outside_unfiltered_divided[["2017.1"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2017.2"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2017.3"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2017.4"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2017.5"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2017.6"]]$delta_VT_t00X)),
                                                             after.outside = c(length(outside_filtered_divided[["2017.1"]]$delta_VT_t00X), length(outside_filtered_divided[["2017.2"]]$delta_VT_t00X), length(outside_filtered_divided[["2017.3"]]$delta_VT_t00X), length(outside_filtered_divided[["2017.4"]]$delta_VT_t00X), length(outside_filtered_divided[["2017.5"]]$delta_VT_t00X), length(outside_filtered_divided[["2017.6"]]$delta_VT_t00X))) %>% mutate(outside.difference = before.outside - after.outside) %>% mutate(percent.outside.difference = (outside.difference/before.outside) * 100)

comparison_of_filtered_unfiltered_outside_2018 <- data.frame(year = 2018, scenario = c(1,2,3,4,5,6),
                                                             before.outside = c(length(may26_outside_unfiltered_divided[["2018.1"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2018.2"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2018.3"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2018.4"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2018.5"]]$delta_VT_t00X), length(may26_outside_unfiltered_divided[["2018.6"]]$delta_VT_t00X)),
                                                             after.outside = c(length(outside_filtered_divided[["2018.1"]]$delta_VT_t00X), length(outside_filtered_divided[["2018.2"]]$delta_VT_t00X), length(outside_filtered_divided[["2018.3"]]$delta_VT_t00X), length(outside_filtered_divided[["2018.4"]]$delta_VT_t00X), length(outside_filtered_divided[["2018.5"]]$delta_VT_t00X), length(outside_filtered_divided[["2018.6"]]$delta_VT_t00X))) %>% mutate(outside.difference = before.outside - after.outside) %>% mutate(percent.outside.difference = (outside.difference/before.outside) * 100)


comparison_of_filtered_unfiltered_outside <- bind_rows(comparison_of_filtered_unfiltered_outside_2017, comparison_of_filtered_unfiltered_outside_2018)


inside_17.001 <- read.csv("./data/csvs/deforested/December2025_17.001_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_17.002 <- read.csv("./data/csvs/deforested/December2025_17.002_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_17.003 <- read.csv("./data/csvs/deforested/December2025_17.003_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_17.004 <- read.csv("./data/csvs/deforested/December2025_17.004_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_17.005 <- read.csv("./data/csvs/deforested/December2025_17.005_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_17.006 <- read.csv("./data/csvs/deforested/December2025_17.006_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.001 <- read.csv("./data/csvs/deforested/December2025_18.001_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.002 <- read.csv("./data/csvs/deforested/December2025_18.002_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.003 <- read.csv("./data/csvs/deforested/December2025_18.003_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.004 <- read.csv("./data/csvs/deforested/December2025_18.004_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.005 <- read.csv("./data/csvs/deforested/December2025_18.005_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)
inside_18.006 <- read.csv("./data/csvs/deforested/December2025_18.006_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(-X) %>% filter(Mean_CTRL_PSN > 2)

may26_inside_17.001 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.001_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 1) %>% select(-X)
may26_inside_17.002 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.002_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 2) %>% select(-X)
may26_inside_17.003 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.003_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 3) %>% select(-X)
may26_inside_17.004 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.004_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 4) %>% select(-X)
may26_inside_17.005 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.005_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 5) %>% select(-X)
may26_inside_17.006 <- read.csv("./data/csvs/csvs_for_revision/May2026_17.006_deforested_points_only.csv") %>% mutate(year = 2017, treatment = 6) %>% select(-X)
may26_inside_18.001 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.001_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 1) %>% select(-X)
may26_inside_18.002 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.002_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 2) %>% select(-X)
may26_inside_18.003 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.003_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 3) %>% select(-X)
may26_inside_18.004 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.004_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 4) %>% select(-X)
may26_inside_18.005 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.005_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 5) %>% select(-X)
may26_inside_18.006 <- read.csv("./data/csvs/csvs_for_revision/May2026_18.006_deforested_points_only.csv") %>% mutate(year = 2018, treatment = 6) %>% select(-X)


comparison_of_filtered_unfiltered_inside_2017 <- data.frame(scenario = c(1,2,3,4,5,6), year = 2017,
                                before.inside = c(length(may26_inside_17.001$delta_VT_t00X), length(may26_inside_17.002$delta_VT_t00X), length(may26_inside_17.003$delta_VT_t00X), length(may26_inside_17.004$delta_VT_t00X), length(may26_inside_17.005$delta_VT_t00X), length(may26_inside_17.006$delta_VT_t00X)),
                                after.inside = c(length(inside_17.001$delta_VT_t00X), length(inside_17.002$delta_VT_t00X), length(inside_17.003$delta_VT_t00X), length(inside_17.004$delta_VT_t00X), length(inside_17.005$delta_VT_t00X), length(inside_17.006$delta_VT_t00X))) %>% mutate(inside.difference = before.inside - after.inside) %>% mutate(percent.inside.difference = (inside.difference/before.inside) * 100)


comparison_of_filtered_unfiltered_inside_2018 <- data.frame(scenario = c(1,2,3,4,5,6), year = 2018,
                                before.inside = c(length(may26_inside_18.001$delta_VT_t00X), length(may26_inside_18.002$delta_VT_t00X), length(may26_inside_18.003$delta_VT_t00X), length(may26_inside_18.004$delta_VT_t00X), length(may26_inside_18.005$delta_VT_t00X), length(may26_inside_18.006$delta_VT_t00X)),
                                after.inside = c(length(inside_18.001$delta_VT_t00X), length(inside_18.002$delta_VT_t00X), length(inside_18.003$delta_VT_t00X), length(inside_18.004$delta_VT_t00X), length(inside_18.005$delta_VT_t00X), length(inside_18.006$delta_VT_t00X))) %>% mutate(inside.difference = before.inside - after.inside) %>% mutate(percent.inside.difference = (inside.difference/before.inside) * 100)

comparison_of_filtered_unfiltered_inside <- bind_rows(comparison_of_filtered_unfiltered_inside_2017, comparison_of_filtered_unfiltered_inside_2018)

comparison_of_filtered_unfiltered <- left_join(comparison_of_filtered_unfiltered_inside, comparison_of_filtered_unfiltered_outside, by = c("year", "scenario"))



comparison_of_filtered_unfiltered_transposed <- comparison_of_filtered_unfiltered %>% mutate(treatment = paste0(year, ", ", scenario)) %>% select(-year) %>% column_to_rownames("treatment") %>% t() %>% as.data.frame()


kable(comparison_of_filtered_unfiltered_transposed, format = "latex", digits = 3, booktabs = TRUE)
```


## Precipitation Validation

```{r}
prism_raster_april17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201704_bil.bil")
prism_raster_may17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201705_bil.bil")
prism_raster_june17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201706_bil.bil")
prism_raster_july17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201707_bil.bil")
prism_raster_august17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201708_bil.bil")
prism_raster_september17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201709_bil.bil")
prism_raster_october17 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2017_all_bil/PRISM_ppt_stable_4kmM3_201710_bil.bil")
prism_raster_april18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201804_bil.bil")
prism_raster_may18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201805_bil.bil")
prism_raster_june18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201806_bil.bil")
prism_raster_july18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201807_bil.bil")
prism_raster_august18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201808_bil.bil")
prism_raster_september18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201809_bil.bil")
prism_raster_october18 <- raster("./data/precip_validation_materials/PRISM_ppt_stable_4kmM3_2018_all_bil/PRISM_ppt_stable_4kmM3_201810_bil.bil")
beginning_of_month_nc_17 <- nc_open("./data/netCDF_files/wrfout_d01_2017-04-01.nc")
end_of_month_nc_17 <- nc_open("./data/netCDF_files/wrfout_d01_2017-11-01.nc")
beginning_of_month_nc_18 <- nc_open("./data/netCDF_files/wrfout_d01_2018-04-01.nc")
end_of_month_nc_18 <- nc_open("./data/netCDF_files/wrfout_d01_2018-11-01.nc")

prism_total17 <- prism_raster_april17 + prism_raster_may17 + prism_raster_june17 + prism_raster_july17 + prism_raster_august17 + prism_raster_september17 + prism_raster_october17
prism_total18 <- prism_raster_april18 + prism_raster_may18 + prism_raster_june18 + prism_raster_july18 + prism_raster_august18 + prism_raster_september18 + prism_raster_october18

lat <- ncvar_get(beginning_of_month_nc_17, "XLAT")
lon <- ncvar_get(beginning_of_month_nc_17, "XLONG")

rainnc_earlier_17 <- ncvar_get(beginning_of_month_nc_17, "RAINNC")
rainnc_17 <- ncvar_get(end_of_month_nc_17, "RAINNC")



rain_increment_17 <- rainnc_17 - rainnc_earlier_17
wrf_raster_17 <- raster(nrows = dim(lat)[1], ncols = dim(lat)[2], xmn = min(lon), xmx = max(lon), ymn = min(lat), ymx = max(lat), crs = "+proj=longlat +datum=WGS84")
new_rain_increment_17 <- rain_increment_17[, ncol(rain_increment_17):1]
values(wrf_raster_17) <- as.vector(new_rain_increment_17)
prism_reprojected_17 <- projectRaster(prism_total17, crs = crs(wrf_raster_17))
prism_resampled_17 <- resample(prism_reprojected_17, wrf_raster_17, method = "bilinear")
bias_17 <- wrf_raster_17 - prism_resampled_17

rainnc_earlier_18 <- ncvar_get(beginning_of_month_nc_18, "RAINNC")
rainnc_18 <- ncvar_get(end_of_month_nc_18, "RAINNC")
rain_increment_18 <- rainnc_18 - rainnc_earlier_18
wrf_raster_18 <- raster(nrows = dim(lat)[1], ncols = dim(lat)[2], xmn = min(lon), xmx = max(lon), ymn = min(lat), ymx = max(lat), crs = "+proj=longlat +datum=WGS84")
new_rain_increment_18 <- rain_increment_18[, ncol(rain_increment_18):1]
values(wrf_raster_18) <- as.vector(new_rain_increment_18)
prism_reprojected_18 <- projectRaster(prism_total18, crs = crs(wrf_raster_18))
prism_resampled_18 <- resample(prism_reprojected_18, wrf_raster_18, method = "bilinear")
bias_18 <- wrf_raster_18 - prism_resampled_18

precip_limits <- range(c(values(wrf_raster_17), values(prism_resampled_17), values(bias_17), values(wrf_raster_18), values(prism_resampled_18), values(bias_18)), na.rm = TRUE)

PRISM_mean_PRCP_17 <- cellStats(prism_resampled_17, stat = 'mean')
PRISM_mean_PRCP_18 <- cellStats(prism_resampled_18, stat = 'mean')
WRF_mean_PRCP_17 <- cellStats(wrf_raster_17, stat = 'mean')
WRF_mean_PRCP_18 <- cellStats(wrf_raster_18, stat = 'mean')
print(paste("PRISM Precipitation Across Focal Domain in 2017:", PRISM_mean_PRCP_17))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", PRISM_mean_PRCP_18))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", WRF_mean_PRCP_17))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", WRF_mean_PRCP_18))

#wrf_raster_17_NONZERO <- wrf_raster_17
#wrf_raster_17_NONZERO[wrf_raster_17_NONZERO <= 313] <- NA
#corrected_bias_17 <- wrf_raster_17_NONZERO - prism_resampled_17
#mean(values(bias_17), na.rm = TRUE)
#mean(values(corrected_bias_17), na.rm = TRUE) ##Straight-up average bias
#sqrt(mean(values(corrected_bias_17)^2, na.rm = TRUE))
#cellStats(wrf_raster_17_NONZERO, stat = 'mean', na.rm = TRUE)
#plot(corrected_bias_17, main = "Bias (WRF - PRISM), April - October, 2017", col = turbo(100), zlim = precip_limits)

par(mfrow = c(2, 3), mar = c(4, 4, 2, 6))
plot(wrf_raster_17, main = "WRF, April - October, 2017", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(prism_resampled_17, main = "PRISM, April - October, 2017", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(bias_17, main = "Bias (WRF - PRISM), April - October, 2017", col = turbo(100), zlim = precip_limits)
plot(wrf_raster_18, main = "WRF, April - October, 2018", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(prism_resampled_18, main = "PRISM, April - October, 2018", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(bias_18, main = "Bias (WRF - PRISM), April - October, 2018", col = turbo(100), zlim = precip_limits)


actual_mean_17 <- cellStats(prism_resampled_17, stat = "mean")
actual_mean_18 <- cellStats(prism_resampled_18, stat = "mean")
wrf_mean_17 <- cellStats(wrf_raster_17, stat = "mean")
wrf_mean_18 <- cellStats(wrf_raster_18, stat = "mean")

diff17 <- wrf_mean_17 / actual_mean_17
diff18 <- wrf_mean_18 / actual_mean_18



lat_cropped <- lat[5:(nrow(lat)-4), 5:(ncol(lat)-4)]
lon_cropped <- lon[5:(nrow(lon)-4), 5:(ncol(lon)-4)]

rainnc_17_earlier_cropped <- rainnc_earlier_17[5:(nrow(rainnc_earlier_17)-4), 5:(ncol(rainnc_earlier_17)-4)]
rainnc_17_cropped <- rainnc_17[5:(nrow(rainnc_17)-4), 5:(ncol(rainnc_17)-4)]

rain_increment_17 <- rainnc_17_cropped - rainnc_17_earlier_cropped

wrf_raster_17 <- raster(nrows = dim(lat_cropped)[1], ncols = dim(lat_cropped)[2], xmn = min(lon_cropped), xmx = max(lon_cropped), ymn = min(lat_cropped), ymx = max(lat_cropped), crs = "+proj=longlat +datum=WGS84")
new_rain_increment_17 <- rain_increment_17[, ncol(rain_increment_17):1]
values(wrf_raster_17) <- as.vector(new_rain_increment_17)
prism_reprojected_17 <- projectRaster(prism_total17, crs = crs(wrf_raster_17))
prism_resampled_17 <- resample(prism_reprojected_17, wrf_raster_17, method = "bilinear")
bias_17 <- wrf_raster_17 - prism_resampled_17

rainnc_18_earlier_cropped <- rainnc_earlier_18[5:(nrow(rainnc_earlier_18)-4), 5:(ncol(rainnc_earlier_18)-4)]
rainnc_18_cropped <- rainnc_18[5:(nrow(rainnc_17)-4), 5:(ncol(rainnc_18)-4)]

rain_increment_18 <- rainnc_18_cropped - rainnc_18_earlier_cropped

wrf_raster_18 <- raster(nrows = dim(lat_cropped)[1], ncols = dim(lat_cropped)[2], xmn = min(lon_cropped), xmx = max(lon_cropped), ymn = min(lat_cropped), ymx = max(lat_cropped), crs = "+proj=longlat +datum=WGS84")
new_rain_increment_18 <- rain_increment_18[, ncol(rain_increment_18):1]
values(wrf_raster_18) <- as.vector(new_rain_increment_18)
prism_reprojected_18 <- projectRaster(prism_total18, crs = crs(wrf_raster_18))
prism_resampled_18 <- resample(prism_reprojected_18, wrf_raster_18, method = "bilinear")
bias_18 <- wrf_raster_18 - prism_resampled_18

precip_limits <- range(c(values(wrf_raster_17), values(prism_resampled_17), values(bias_17), values(wrf_raster_18), values(prism_resampled_18), values(bias_18)), na.rm = TRUE)

PRISM_mean_PRCP_17 <- cellStats(prism_resampled_17, stat = 'mean')
PRISM_mean_PRCP_18 <- cellStats(prism_resampled_18, stat = 'mean')
WRF_mean_PRCP_17 <- cellStats(wrf_raster_17, stat = 'mean')
WRF_mean_PRCP_18 <- cellStats(wrf_raster_18, stat = 'mean')
print(paste("PRISM Precipitation Across Focal Domain in 2017:", PRISM_mean_PRCP_17))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", PRISM_mean_PRCP_18))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", WRF_mean_PRCP_17))
print(paste("PRISM Precipitation Across Focal Domain in 2018:", WRF_mean_PRCP_18))

#wrf_raster_17_NONZERO <- wrf_raster_17
#wrf_raster_17_NONZERO[wrf_raster_17_NONZERO <= 313] <- NA
#corrected_bias_17 <- wrf_raster_17_NONZERO - prism_resampled_17
#mean(values(bias_17), na.rm = TRUE)
#mean(values(corrected_bias_17), na.rm = TRUE) ##Straight-up average bias
#sqrt(mean(values(corrected_bias_17)^2, na.rm = TRUE))
#cellStats(wrf_raster_17_NONZERO, stat = 'mean', na.rm = TRUE)
#plot(corrected_bias_17, main = "Bias (WRF - PRISM), April - October, 2017", col = turbo(100), zlim = precip_limits)

pdf("~/Desktop/S1_PrecipValidation.pdf", width = 9.45, height = 5.2)
par(mfrow = c(2, 3), mar = c(4, 4, 2, 6))
plot(wrf_raster_17, main = "WRF, April - October, 2017", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(prism_resampled_17, main = "PRISM, April - October, 2017", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(bias_17, main = "Bias (WRF - PRISM), April - October, 2017", col = turbo(100), zlim = precip_limits)
plot(wrf_raster_18, main = "WRF, April - October, 2018", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(prism_resampled_18, main = "PRISM, April - October, 2018", col = turbo(100), zlim = precip_limits, xlim = range(lat))
plot(bias_18, main = "Bias (WRF - PRISM), April - October, 2018", col = turbo(100), zlim = precip_limits)
dev.off()

actual_mean_17 <- cellStats(prism_resampled_17, stat = "mean")
actual_mean_18 <- cellStats(prism_resampled_18, stat = "mean")
wrf_mean_17 <- cellStats(wrf_raster_17, stat = "mean")
wrf_mean_18 <- cellStats(wrf_raster_18, stat = "mean")

diff17 <- wrf_mean_17 / actual_mean_17
diff18 <- wrf_mean_18 / actual_mean_18

```



